---
title: "N-back Preprocessing"
author: "Michael Colwell"
date: '22/03/2024'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### N-back DDM + neuroimaging data processing  scripts for the PEACE Study ('Pitolisant Effects on Affect and Cognition Exploratory Study') (NCT05849675). 

This an R Markdown file was created by Michael Colwell (michael.colwell@psych.ox.ac.uk / ORCID 0000-0001-7846-2879), based on a task from the same author: https://github.com/mjcolwell/n-back_oxford/releases/tag/Python

#This script includes: 

- Preprocessing of DDM parameter values
- DDM inferrential analysis (between-groups)
- DDM parameter recovery
- DDM posterior predictive checks
- Secondary DDM analysis: Non-decision time (median-split) and task performance analysis
- DDM parameter v ~ fMRI beta value (linear model of increasing complexity) analysis
- Supplementary analysis

For the behavioural (non-model) analysis of the N-back task, and associated neuroimaging analysis, please see the 'N_Back_fMRI/fMRI_nback_PreProcessing_and_Analysis.Rmd' file.

## Quality check and analysis scripts for OMT data in FENCOG project.

```{r libraries, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggplot2)
library(car)
library(ggbeeswarm)
library(ggrepel)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(sdamr)
library(cowplot)
library(lme4)
library(stringr)
library(effectsize)
library(lmerTest)
library(ggridges)
library(viridis)
library(ggstance)
library(ggdist)
library(gghalves)
library(ggpp)
library(readxl)
library(purrr)
library(broom)
library(ggExtra)
library(moments)
```

## Set Dir and load in file

```{r b0, echo=FALSE, include=TRUE}
setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/NBack_DDM")

MasterDDM <- read.csv("Group_Data_Levels.csv", header = TRUE, stringsAsFactors = FALSE)
```

##Parsing + Demographic inclusion

```{r b0, echo=FALSE, include=TRUE}
# Log transform decision policy to maintain consistency across DDM analyses

MasterDDM$a.1. <- log(MasterDDM$a)

# Arcscin transform non-decision time to maintain consistency across analyses
MasterDDM$t.a <- asin(sqrt(MasterDDM$t))

## Demographics

MasterDDM_2 <- MasterDDM

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics/")

Demographics <- read.csv("Allocation_And_Demo.csv")

Demographics$Participant.ID <- as.factor(Demographics$Participant.ID)

MasterDDM <- merge(MasterDDM, Demographics, by = "Participant.ID")

removal_df <- subset(MasterDDM, Participant.ID != "P001" & Participant.ID != "P009" & Participant.ID != "P011" & Participant.ID != "P025" & Participant.ID != "P037" & Participant.ID != "P059")

# Removal of outliers agreed prior to unblinding. These are outliers who performed poorly on the task or displayed irrecoverably high motion during task performance or complained they were unable to see the stimuli due to improper vision correction. No behavioural outliers were observed in the data quality report.

MasterDDM <- droplevels(removal_df)
```

##Graphs for publication

```{r Chunk 7 - Generation of figures for report, echo=FALSE}
ci95 <- function(x) {
  error <- qt(0.975, df = length(x) - 1) * sd(x) / sqrt(length(x))
  return(error)
}

v_Fig <- MasterDDM %>%
  group_by(Allocation, condition) %>%
  summarize(value = mean(v), SE = std.error(v)) %>%
  ggplot(aes(condition, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = condition, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.4, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.4) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "") +
  ylab("Drift rate v\n") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", axis.text = element_text(size = 14), axis.title = element_text(size = 16)) +
  scale_shape_manual(values = c(19, 15))

t_Fig <- MasterDDM %>%
  group_by(Allocation, condition) %>%
  summarize(value = mean(t.a), SE = std.error(t.a)) %>%
  ggplot(aes(condition, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = condition, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.4, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.4) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "") +
  ylab("Non-decision time TeR\n") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "left", axis.text = element_text(size = 14), axis.title = element_text(size = 16), axis.text.x = element_blank()) +
  scale_shape_manual(values = c(19, 15))

a_Fig <- MasterDDM %>%
  group_by(Allocation, condition) %>%
  summarize(value = mean(a.1.), SE = std.error(a.1.)) %>%
  ggplot(aes(condition, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = condition, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.4, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.4) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "") +
  ylab("Log decision policy (a)\n") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "None", axis.text = element_text(size = 14), axis.title = element_text(size = 16)) +
  scale_shape_manual(values = c(19, 15))
````
  

```{r b0, echo=FALSE, include=TRUE}
# ANCOVA model setup and analysis

# Drift rate

ANCOVA_v <- aov(v ~ Allocation + condition + Allocation:condition + Error(Participant.ID), data = MasterDDM)

summary(ANCOVA_v)

# Significant

model_linear <- lmer(v ~ Allocation + condition + Allocation:condition + (1 | Participant.ID), data = MasterDDM)

summary(model_linear)

anova(model_linear, type = 2) # Type III ANOVA-like table

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | condition)

confint(model_linear, method = "Wald")

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

#########

# Decision policy

ANCOVA_Boundary <- aov(a ~ Allocation + condition + Allocation:condition + Error(Participant.ID), data = MasterDDM)

summary(ANCOVA_Boundary)

# Not significant

# Non-decision time.

ANCOVA_Drift <- aov(t.a ~ Allocation + condition + Allocation:condition + Error(Participant.ID), data = MasterDDM)

summary(ANCOVA_Drift)

# Significant

model_linear <- lmer(t.a ~ Allocation + condition + Allocation:condition + (1 | Participant.ID), data = MasterDDM)

summary(model_linear)

anova(model_linear, type = 2) # Type III ANOVA-like table

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | condition)

confint(model_linear, method = "Wald")

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

####
```

```{r b0, echo=FALSE, include=TRUE}
###

# DDM parameter v ~ fMRI beta value (linear model of increasing complexity) analysis

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/ROI_Data/")

ROI_sign <- read.csv("n_back_sig_clusters_PE.csv")

Master_Scatter_f <- MasterDDM %>%
  group_by(Participant.ID, Allocation) %>%
  summarize(
    v = mean(v, na.rm = TRUE),
    t.1. = mean(t.a, na.rm = TRUE),
    st = mean(st, na.rm = TRUE)
  )


Master_Scatter_f <- merge(Master_Scatter_f, ROI_sign, by = "Participant.ID")

###

LM_1 <- lm(v ~ H3R_Linear, data = Master_Scatter_f)

summary(LM_1)

cor_result <- cor.test(Master_Scatter_f$v, Master_Scatter_f$H3R_Linear)

eta_squared(LM_1, ci = 0.95, alternative = "two.sided")

# Fit regression within each sample
regression_results <- Master_Scatter_f %>%
  group_by(Allocation) %>%
  group_map(~ tidy(lm(v ~ H3R_Linear, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

# Figure 4G

# Compute correlation coefficient and p-value
cor_result <- cor.test(Master_Scatter_f$v, Master_Scatter_f$H3R_Linear)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Master_Scatter_f, aes(x = v, y = H3R_Linear)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nDrift Rate v\n",
    y = "\nLinear Complexity Signal (Left DLPFC)\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Figure_4G <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)
```


```{r b0, echo=FALSE, include=TRUE}
#### PE Estimates figures

# Supplementary Figure 11

Linear_Beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = Linear_L_Caud_New, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Increasing Complexity lDLPFC Beta\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

DLPFC_Beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = L_DLPFC_2B, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("lDLPFC beta (0>2-back)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Hipp_Beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = TWOBACK_Hipp, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Bil. Hippocampus beta (0>2-back)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

SN_Beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = TWOBACK_SN, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Substantia Nigra beta (0>2-back)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Basalf_Beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = TWOBACK_Basal_F, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Basal forebrain beta (0>2-back)\n\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

three_back_beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = Caud_L_New_3Back, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Left DLPFC beta (0>3-back)\n\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))


one_back_beta <- Master_Scatter_f %>% ggplot(aes(x = Allocation, y = Caud_L_New_1Back, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Left DLPFC beta (0>1-back)\n\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Supp.Fig.11 <- plot_grid(Linear_Beta, one_back_beta, DLPFC_Beta, three_back_beta, Hipp_Beta, SN_Beta, Basalf_Beta)
```


```{r b0, echo=FALSE, include=TRUE}
# Initial Posterior Predictive Checks - Synthetic and real data comparison

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/NBack_DDM")

PP_Data <- read.csv("posterior_nback_data.csv", header = TRUE, stringsAsFactors = FALSE)

# Define new row names (make sure the length matches the number of rows)

PP_Combined_Summary <- PP_Data %>%
  group_by(subj_idx, condition, Data_Type) %>%
  summarise(Response.time = mean(rt, na.rm = TRUE), Accuracy = mean(correct, na.rm = TRUE))

# Figure 3C

# PP check graph - RT

RT_Graph <- ggplot(PP_Combined_Summary, aes(x = Response.time, fill = Data_Type, linetype = Data_Type)) +
  geom_density(alpha = 0.4, size = 1.1) +
  theme_minimal() +
  xlab("\nTime to Choice (ms)\n") +
  ylab("\nP(Density)\n") +
  xlim(NA, 2) +
  theme(legend.position = "none", text = element_text(size = 14), axis.title = element_text(size = 16))

# PP check graph - Accuracy

Correct_Graph <- ggplot(PP_Combined_Summary, aes(x = Accuracy, fill = Data_Type, linetype = Data_Type)) +
  geom_density(alpha = 0.4, size = 1.1) +
  theme_minimal() +
  xlab("\nOverall Accuracy\n") +
  ylab("\nP(Density)\n") +
  theme(legend.position = "none", text = element_text(size = 14), axis.title = element_text(size = 16))

combined <- plot_grid(RT_Graph, Correct_Graph, cols = 1)

#################################
```



```{r b0, echo=FALSE, include=TRUE}
# Parameter recovery - loading in file + graph generation

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/NBack_DDM/")

MasterDDM_sim <- read.csv("param_recovery.csv", header = TRUE, stringsAsFactors = FALSE)

MasterDDM_sim$a <- log(MasterDDM_sim$a)

# Graph generation

##### Param recovery plots(Supplementaty Fig. 8)

MasterDDM_sim$Blank <- "Blank"

BoundarySep <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = a, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Log boundary separation (a)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = log(0.5), linetype = "dashed", color = "orange", size = 1)

DriftRate <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = v, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Drift rate (v)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.45, linetype = "dashed", color = "orange", size = 1) +
  ylim(NA, 2.9)

NonDec <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = asin(sqrt(MasterDDM_sim$t)), fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Non-decision time (Ter)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = asin(sqrt(0.15)), linetype = "dashed", color = "orange", size = 1)

var_v <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = sv, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Inter-trial drift rate variability (sv)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 2, linetype = "dashed", color = "orange", size = 1)

var_ter <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = st, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Inter-trial non-decision time variability (st)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "orange", size = 1)

SuppFig8 <- plot_grid(BoundarySep, DriftRate, NonDec, var_v, var_ter, align = "v", ncol = 5, labels = c(""), label_size = 20)
```



```{r b0, echo=FALSE, include=TRUE}
# Secondary DDM analysis: Non-decision time (median-split) and task performance analysis - posterior analysis

# Parse PP df

Posterior_Summaries <- PP_Data

Posterior_Summaries <- Posterior_Summaries %>%
  rename(Participant.ID = subj_idx)

Posterior_Summaries <- Posterior_Summaries %>%
  mutate(qtarget_corr_acc = case_when(
    stimulus == 1 & correct == 1 ~ 1,
    stimulus == 1 & correct == 0 ~ 0,
    TRUE ~ NA_real_
  ))

Posterior_Summaries <- Posterior_Summaries %>%
  mutate(no_qtarget_incorr_acc = case_when(
    stimulus == 0 & correct == 1 ~ 0,
    stimulus == 0 & correct == 0 ~ 1,
    TRUE ~ NA_real_
  ))

Posterior_Summaries_Avg <- Posterior_Summaries %>%
  group_by(Participant.ID, condition, Data_Type) %>%
  summarise(
    response.time = mean(rt, na.rm = TRUE),
    response = sum(response, na.rm = TRUE),
    correct = mean(correct, na.rm = TRUE),
    stimulus = sum(stimulus, na.rm = TRUE),
  )

Posterior_Summaries_Avg$correct <- Posterior_Summaries_Avg$correct * 100

Posterior_Summaries_Avg$correct_log <- log(Posterior_Summaries_Avg$correct)

posterior_draws_avg <- subset(Posterior_Summaries_Avg, Data_Type != "Real")

removal_df <- subset(posterior_draws_avg, Participant.ID != "P001" & Participant.ID != "P009" & Participant.ID != "P011" & Participant.ID != "P025" & Participant.ID != "P037" & Participant.ID != "P059")

posterior_draws_avg <- droplevels(removal_df)

posterior_draws_avg_w_params <- merge(posterior_draws_avg, MasterDDM, by = c("Participant.ID", "condition"), all = TRUE)

# Non-decision time: within-subjects median split

posterior_draws_avg_w_params <- posterior_draws_avg_w_params %>%
  group_by(Participant.ID) %>%
  mutate(
    t_med_i = median(t.a, na.rm = TRUE),
    t_bin   = if_else(t.a < t_med_i, "Low", "High"),
    t_bin   = factor(t_bin, levels = c("Low", "High"))
  ) %>%
  ungroup() %>%
  select(-t_med_i)

posterior_draws_avg_w_params$t_bin <- factor(
  posterior_draws_avg_w_params$t_bin,
  levels = c("High", "Low")
)

# Checking distribution values

x <- posterior_draws_avg_w_params$correct

# skewness
skew_val <- skewness(x, na.rm = TRUE)

kurt_val <- kurtosis(x, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)

# To keep consistency with observed data, accuracy values were log-transformed:

posterior_draws_avg_w_params$correct_log <- log(posterior_draws_avg_w_params$correct)

# Figure for publication - Figure 3C - lower right

Figure3C_lowerright <- posterior_draws_avg_w_params %>%
  group_by(t_bin, condition) %>%
  summarize(value = mean(correct), SE = std.error(correct)) %>%
  ggplot(aes(condition, value, group = t_bin)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = condition, ymin = value - SE, ymax = value + SE, color = t_bin), width = 0.25) +
  geom_point(aes(color = t_bin, shape = t_bin), size = 2.4, alpha = 0.8) +
  geom_line(aes(color = t_bin, linetype = t_bin), size = 1.4) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = t_bin
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "") +
  ylab("Posterior accuracy (%)\n") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "None", axis.text = element_text(size = 14), axis.title = element_text(size = 16)) +
  scale_shape_manual(values = c(19, 15))

# Inferential analysis

ANCOVA_Drift <- aov(correct_log ~ t_bin + condition + t_bin:condition + Error(Participant.ID), data = posterior_draws_avg_w_params)

summary(ANCOVA_Drift)

model_linear <- lmer(correct_log ~ t_bin + condition + t_bin:condition + (1 | Participant.ID), data = posterior_draws_avg_w_params)

# Due to high non-normality, EMM values were bootstrapped (in addition to log-transormed. For interpretability, figures show non-log transformed values.)

# Returns: contrast, estimate, SE_boot, CI_lower, CI_upper, p_boot  (+ optional SE_wald)
bootstrap_emm_contrasts <- function(model, nsim = 5000, seed = 111, include_wald_se = TRUE) {
  set.seed(seed)

  # 1) Point estimates & (optional) Wald SE from current model
  emm_ref <- emmeans(model, ~ t_bin | condition)
  contr_ref <- as.data.frame(pairs(emm_ref, adjust = "none")) # all within-condition pairs
  est <- contr_ref$estimate
  labs <- paste(contr_ref$contrast, "|", contr_ref$condition)
  K <- length(est)

  SE_wald <- if (include_wald_se) contr_ref$SE else NULL

  # 2) Bootstrap the SAME contrasts
  boot_contr <- bootMer(
    model,
    FUN = function(fit) {
      cr <- as.data.frame(pairs(emmeans(fit, ~ t_bin | condition), adjust = "none"))
      as.numeric(cr$estimate) # numeric length K
    },
    nsim = nsim,
    use.u = TRUE,
    type = "parametric",
    seed = seed
  )

  boot_mat <- as.matrix(boot_contr$t) # B x K
  stopifnot(ncol(boot_mat) == K)
  B <- nrow(boot_mat)

  # 3) Bootstrap SEs and percentile CIs
  SE_boot <- apply(boot_mat, 2, sd, na.rm = TRUE)
  ci <- apply(boot_mat, 2, quantile, probs = c(.025, .975), na.rm = TRUE)

  # 4) Two-sided bootstrap p-values (+1 correction avoids exact zeros)
  p_boot <- sapply(seq_len(K), function(j) {
    dj <- boot_mat[, j]
    lo <- sum(dj <= 0, na.rm = TRUE)
    hi <- sum(dj >= 0, na.rm = TRUE)
    2 * min((lo + 1) / (B + 1), (hi + 1) / (B + 1))
  })

  out <- tibble(
    contrast = labs,
    estimate = est,
    SE_boot  = SE_boot,
    CI_lower = ci[1, ],
    CI_upper = ci[2, ],
    p_boot   = p_boot
  )

  if (include_wald_se) {
    out <- mutate(out, SE_wald = SE_wald, .after = estimate)
  }

  out
}

# Run it
results <- bootstrap_emm_contrasts(model_linear, nsim = 5000, seed = 111)
results

### Checking RT effects across ter bins

ANCOVA_Drift <- aov(response.time ~ t_bin + condition + t_bin:condition + Error(Participant.ID), data = posterior_draws_avg_w_params)

summary(ANCOVA_Drift)


### Checking continuous t.a values relationship with performance.

ANCOVA_Drift <- lmer(t.a ~ correct_log * condition + (1 | Participant.ID), data = posterior_draws_avg_w_params)

summary(ANCOVA_Drift)

standardize_parameters(ANCOVA_Drift)

# Remains significant with allocation included:

ANCOVA_Drift <- lmer(t.a ~ correct_log * condition + Allocation + (1 | Participant.ID), data = posterior_draws_avg_w_params)

summary(ANCOVA_Drift)

standardize_parameters(ANCOVA_Drift)
```

```{r b0, echo=FALSE, include=TRUE}
# Secondary DDM analysis: Non-decision time (median-split) and task performance analysis - observed data analysis

# Checking distribution

# numeric vector (your variable of interest)
x <- MasterDDM$Overall_acc_perc

# skewness
skew_val <- skewness(x, na.rm = TRUE)

kurt_val <- kurtosis(x, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)

# ensure t.a is numeric
MasterDDM <- MasterDDM %>% mutate(t.a = as.numeric(t.a))

# Non-decision time: within-subjects median split

MasterDDM <- MasterDDM %>%
  group_by(Participant.ID) %>%
  mutate(
    t_med_i = median(t.a, na.rm = TRUE),
    t_bin   = if_else(t.a < t_med_i, "Low", "High"),
    t_bin   = factor(t_bin, levels = c("Low", "High"))
  ) %>%
  ungroup() %>%
  select(-t_med_i)

# quick sanity checks
table(MasterDDM$t_bin, useNA = "ifany")
MasterDDM %>%
  count(Participant.ID, t_bin) %>%
  tidyr::pivot_wider(names_from = t_bin, values_from = n, values_fill = 0) %>%
  print(n = 10)

# As with main analysis, accuracy values were log-transformed

MasterDDM$Overall_acc_perc_log <- log(MasterDDM$Overall_acc_perc)

# Inferential analysis

ANCOVA_Drift <- aov(Overall_acc_perc_log ~ t_bin + condition + t_bin:condition + Error(Participant.ID), data = MasterDDM)

summary(ANCOVA_Drift)

# Results are significant with allocation included as a regressor.
model_linear <- lmer(Overall_acc_perc_log ~ t_bin + condition + t_bin:condition + (1 | Participant.ID), data = MasterDDM)

# Due to high non-normality, EMM values were bootstrapped (in addition to log-tranfsormed. For interpretability, figures show non-log transformed values.)

# Returns: contrast, estimate, SE_boot, CI_lower, CI_upper, p_boot  (+ optional SE_wald)
bootstrap_emm_contrasts <- function(model, nsim = 5000, seed = 111, include_wald_se = TRUE) {
  set.seed(seed)

  # 1) Point estimates & (optional) Wald SE from current model
  emm_ref <- emmeans(model, ~ t_bin | condition)
  contr_ref <- as.data.frame(pairs(emm_ref, adjust = "none")) # all within-condition pairs
  est <- contr_ref$estimate
  labs <- paste(contr_ref$contrast, "|", contr_ref$condition)
  K <- length(est)

  SE_wald <- if (include_wald_se) contr_ref$SE else NULL

  # 2) Bootstrap the SAME contrasts
  boot_contr <- bootMer(
    model,
    FUN = function(fit) {
      cr <- as.data.frame(pairs(emmeans(fit, ~ t_bin | condition), adjust = "none"))
      as.numeric(cr$estimate) # numeric length K
    },
    nsim = nsim,
    use.u = TRUE,
    type = "parametric",
    seed = seed
  )

  boot_mat <- as.matrix(boot_contr$t) # B x K
  stopifnot(ncol(boot_mat) == K)
  B <- nrow(boot_mat)

  # 3) Bootstrap SEs and percentile CIs
  SE_boot <- apply(boot_mat, 2, sd, na.rm = TRUE)
  ci <- apply(boot_mat, 2, quantile, probs = c(.025, .975), na.rm = TRUE)

  # 4) Two-sided bootstrap p-values (+1 correction avoids exact zeros)
  p_boot <- sapply(seq_len(K), function(j) {
    dj <- boot_mat[, j]
    lo <- sum(dj <= 0, na.rm = TRUE)
    hi <- sum(dj >= 0, na.rm = TRUE)
    2 * min((lo + 1) / (B + 1), (hi + 1) / (B + 1))
  })

  out <- tibble(
    contrast = labs,
    estimate = est,
    SE_boot  = SE_boot,
    CI_lower = ci[1, ],
    CI_upper = ci[2, ],
    p_boot   = p_boot
  )

  if (include_wald_se) {
    out <- mutate(out, SE_wald = SE_wald, .after = estimate)
  }

  out
}

# Run it
results <- bootstrap_emm_contrasts(model_linear, nsim = 5000, seed = 111)
results

### Checking RT effect

ANCOVA_Drift <- aov(mean_RT_all ~ t_bin + condition + t_bin:condition + Error(Participant.ID), data = MasterDDM)

summary(ANCOVA_Drift)

####

# Supplementary Figure 9C

Supp.fig9C <- MasterDDM %>%
  group_by(t_bin, condition) %>%
  summarize(value = mean(Overall_acc_perc), SE = std.error(Overall_acc_perc)) %>%
  ggplot(aes(condition, value, group = t_bin)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = condition, ymin = value - SE, ymax = value + SE, color = t_bin), width = 0.25) +
  geom_point(aes(color = t_bin, shape = t_bin), size = 2.4, alpha = 0.8) +
  geom_line(aes(color = t_bin, linetype = t_bin), size = 1.4) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = t_bin
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "") +
  ylab("Posterior accuracy (%)\n") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "None", axis.text = element_text(size = 14), axis.title = element_text(size = 16)) +
  scale_shape_manual(values = c(19, 15))

Supp.fig9C

### Checking continuous t.a values relationship with observed performance.

ANCOVA_Drift <- lmer(t.a ~ Overall_acc_perc * condition + (1 | Participant.ID), data = MasterDDM)

summary(ANCOVA_Drift)

standardize_parameters(ANCOVA_Drift)

ANCOVA_Drift <- lmer(t.a ~ Overall_acc_perc * condition + Allocation + (1 | Participant.ID), data = MasterDDM)

summary(ANCOVA_Drift)

standardize_parameters(ANCOVA_Drift)
``````
