---
title: "PILT_Comp_Analysis_FENCOG"
author: "Michael Colwell"
date: '2023-04-09'
output: html_document
---

##PILT pre-processing script

This is the computational modelling analysis for the Probabilistic Instrumental Learning Task (PILT), modified for the PEACE study by Michael Colwell (michael.colwell@psych.ox.ac.uk).

Computational models were generated via scripts contained in the './Behavioural_Data/PILT_fitting_scripts/' folder. For the behavioural data analysis, please see './PILT_nonmodel/PILT_data preprocessing_and_analysis.Rmd'.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quality check and analysis scripts for OMT data in FENCOG project.

```{r libraries, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggplot2)
library(car)
library(ggbeeswarm)
library(ggrepel)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(sdamr)
library(cowplot)
library(lme4)
library(stringr)
library(cowplot)
library(lme4)
library(effectsize)
library(lmerTest)
library(ggdist)
library(ggExtra)
```

## Set Dir and load in file

```{r b0, echo=FALSE, include=TRUE}
setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/PILT_Reinforcement_Learning_Mod")

MasterPILTc <- read.csv("Reinforcement_Learning_PILT_full.csv", header = TRUE, stringsAsFactors = FALSE)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

Merged_MemROI <- merge(MasterPILTc, Allocation_and_Demographics, by = "Participant.ID")

# Log transform LR -- you don't need to log transform beta, the fitting script is already doing this.

Merged_MemROI$LR_recipmodel <- log(Merged_MemROI$LR_recipmodel)
Merged_MemROI$Excl10_LR <- log(Merged_MemROI$Excl10_LR)

## P012 was identified pre-identified as having issues related to task performance (i.e., was aware of exact probabilities and task structure)

removal_df <- subset(Merged_MemROI, Participant.ID != "P012")

Merged_MemROI <- droplevels(removal_df)
```

##Graphs for publication

```{r Chunk 7 - Generation of figures for report, echo=FALSE}
# MasterPILTc_CPostLoss <- MasterPILTc_CPost %>% filter(!str_deteParticipant.ID# MasterPILTc_CPostLoss <- MasterPILTc_CPost %>% filter(!str_detect(Trial_type, "Reward"))

Merged_MemROI <- Merged_MemROI %>%
  mutate(Trial_type = factor(Trial_type, levels = c("Win", "Loss")))

### Outcome sensitivity across trial types at follow-up - Supplementary Fig. 14B

# EEM removed to reflect lack of ANOVA difference.

SuppFig14B <- Merged_MemROI %>% ggplot(aes(x = Allocation, y = inv_recipmodel, fill = Allocation)) +
  facet_wrap(~Trial_type) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("*" = 0.001, "*" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Log outcome sensitivity (ρ)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

# Figure 5E

# Plot to demonstrate LR interaction effect
Fig5E <- ggplot(Merged_MemROI, aes(x = Trial_type, y = inv_recipmodel, color = Allocation, group = Allocation)) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  # Left side (for 'Loss')
  stat_slab(
    data = subset(Merged_MemROI, Trial_type == "Loss"), # Only data where Trial_type is 'Loss'
    side = "left", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = -0.15)
  ) +

  # Right side (for 'Win')
  stat_slab(
    data = subset(Merged_MemROI, Trial_type == "Win"), # Only data where Trial_type is 'Win'
    side = "right", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = 0.15)
  ) +
  geom_line(aes(group = Participant.ID), linetype = "dashed", size = 0.175, alpha = 0.50) +

  # Points and lines (jittered and connected by Participant.ID)
  geom_point(position = position_jitternudge(
    jitter.width = 0.2, jitter.height = -0.3, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.15, alpha = 0.55) +

  # Lines connecting points for each Participant.ID (grouping)

  # Labels and title
  labs(
    title = "",
    x = "",
    y = "\nLog learning rate (α)\n"
  ) +
  theme_minimal()
````
  

```{r b0, echo=FALSE, include=TRUE}
# ANCOVA model setup and analysis

## Learning rate

# . As α and β covary within fitted models, inferential models included the reciprocal parameter as a random effect. See Supplementary Methods for further details.

model_check <- lmer(LR_recipmodel ~ Allocation * Trial_type + (1 + inv_recipmodel || Participant.ID), data = Merged_MemROI)

aov_mod <- anova(model_check)

aov_mod

eta_squared(test, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_check, ~ Allocation | Trial_type)

pairs(EMM_2, adjust = "holm")

## Inverse decision temperature

model_check <- lmer(inv_recipmodel ~ Allocation * Trial_type + (1 + LR_recipmodel || Participant.ID), data = Merged_MemROI)

aov_mod <- anova(model_check)

aov_mod

eta_squared(test, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_check, ~ Allocation | Trial_type)

pairs(EMM_2, adjust = "holm")

# get posterior draws of marginal means
emm <- emmeans(m_lr, ~ Allocation | Trial_type)

# summary with credible intervals
summary(emm, infer = c(TRUE, TRUE), level = 0.95, type = "response")

# pairwise contrasts if needed
pairs(emm, adjust = "holm")

## Checking relationship between RL params and behavioural performance

d <- lmer(Optimal.choice.perc ~ LR_recipmodel * Trial_type + (1 | Participant.ID), data = Merged_MemROI)

eta_squared(d, ci = 0.95, alternative = "two.sided")

# Fit regression within each sample
regression_results <- Merged_MemROI %>%
  group_by(Allocation) %>%
  group_map(~ tidy(lm(Optimal.choice.perc ~ LR_recipmodel, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

# Figure 5F

# Compute correlation coefficient and p-value
cor_result <- cor.test(Merged_MemROI$Optimal.choice.perc, Merged_MemROI$LR_recipmodel)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Merged_MemROI, aes(x = Optimal.choice.perc, y = LR_recipmodel)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nOptimal Choices (%) - Observed\n",
    y = "\nLog learning rate\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.55) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Fig5F <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)
```

```{r b0, echo=FALSE, include=TRUE}
# Posterior check

# Remove P012 to keep consistency with the observed data analysis.

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/PILT_Reinforcement_Learning_Mod/")

Posterior_Summaries <- read.csv("Posteriors.csv", header = TRUE, stringsAsFactors = FALSE)

removal_df <- subset(Posterior_Summaries, Participant.ID != "P012")

Posterior_Summaries <- droplevels(removal_df)

Posterior_Summaries <- Posterior_Summaries %>% filter(Trial_No > 19)

Posterior_Summaries_Avg <- Posterior_Summaries %>%
  group_by(Participant.ID, Trial_type) %>%
  summarise(Choice.prob_post = mean(Choice.prob, na.rm = TRUE))

Posterior_Summaries_Avg_Merged <- merge(
  Posterior_Summaries_Avg,
  Merged_MemROI,
  by = c("Participant.ID", "Trial_type")
)

Posterior_Summaries_Avg_Merged$Choice.prob_post <- Posterior_Summaries_Avg_Merged$Choice.prob_post * 100

d <- lmer(Choice.prob_post ~ LR_recipmodel * Trial_type + (1 | Participant.ID), data = Posterior_Summaries_Avg_Merged)

# Fit regression within each sample
regression_results <- Posterior_Summaries_Avg_Merged %>%
  group_by(Allocation) %>%
  group_map(~ tidy(lm(Choice.prob_post ~ LR_recipmodel, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

# Supplementary Fig 14C

# Compute correlation coefficient and p-value
cor_result <- cor.test(Posterior_Summaries_Avg_Merged$Choice.prob_post, Posterior_Summaries_Avg_Merged$LR_recipmodel)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Posterior_Summaries_Avg_Merged, aes(x = Choice.prob_post, y = LR_recipmodel)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nOptimal Choices (%) - Posterior\n",
    y = "\nLog learning rate\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

SuppFig14C <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)
```

```{r b0, echo=FALSE, include=TRUE}
# Check inferential model with first 10 trials (per trial type) excluded in fitting script

model_check <- lmer(Excl10_LR ~ Allocation * Trial_type + (1 + Excl10_Inv || Participant.ID), data = Merged_MemROI)

aov_mod <- anova(model_check)

aov_mod

EMM_2 <- emmeans(model_check, ~ Allocation | Trial_type)

pairs(EMM_2, adjust = "holm")

effect_size <- eff_size(EMM_2, sigma = sigma(model_check), edf = df.residual(model_check))

summary(effect_size)

model_check <- lmer(Excl10_Inv ~ Allocation * Trial_type + (1 + Excl10_LR || Participant.ID), data = Merged_MemROI)

aov_mod <- anova(model_check)

aov_mod
```

```{r b0, echo=FALSE, include=TRUE}
## Generate posterior learning curve

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/PILT_Reinforcement_Learning_Mod")

PosteriorLearning <- read.csv("Posteriors.csv", header = TRUE, stringsAsFactors = FALSE)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

PosteriorLearning_M <- merge(PosteriorLearning, Allocation_and_Demographics, by = "Participant.ID")

# Log transform LR -- you don't need to log transform beta, the fitting script is already doing this.

## P012 was identified pre-identified as having issues related to task performance (i.e., was aware of exact probabilities and task structure)

removal_df <- subset(PosteriorLearning_M, Participant.ID != "P012")

PosteriorLearning_M <- droplevels(removal_df)

## Simulate choices via Bernoulli trial sampling

set.seed(123) # optional for reproducibility

PosteriorLearning_M <- PosteriorLearning_M %>%
  ungroup() %>%
  mutate(
    p_one = if_else(Trial_type == "Loss", 1 - Choice.prob, Choice.prob),
    SimChoice = rbinom(n(), size = 1, prob = p_one)
  ) %>%
  select(-p_one)

# Summary at group level

PosteriorLearning_M_R <- PosteriorLearning_M %>%
  group_by(Allocation, Trial_type, Trial_No) %>%
  summarise(Optimal.choice = mean(SimChoice, na.rm = TRUE) * 100, SE = sd(SimChoice, na.rm = TRUE) / sqrt(n()) * 100)

# Generate curve

CurveUnified <- ggplot(
  PosteriorLearning_M_R,
  aes(
    x = Trial_No, y = Optimal.choice,
    group = interaction(Trial_type, Allocation),
    colour = Allocation, linetype = Allocation
  )
) +
  geom_segment(aes(x = 10, xend = 30, y = 50, yend = 50),
    linetype = "dotted", color = "azure3"
  ) +
  geom_vline(xintercept = 10, linetype = "dotted", color = "azure3") +
  geom_ribbon(
    aes(
      ymin = Optimal.choice - SE,
      ymax = Optimal.choice + SE,
      fill = Allocation
    ),
    color = NA, alpha = 0.11, show.legend = FALSE
  ) +
  geom_line(linewidth = 0.7) +
  geom_point(aes(shape = Allocation), size = 2.75, alpha = 0.77) +
  theme_minimal() +
  scale_shape_manual(values = c(19, 15)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  ylab("High probability stimulus selected (%)\n") +
  xlab("Trial number\n") +
  annotate("text", x = 15, y = 70, label = "\nWin trials", size = 3.5, color = "#333333") +
  annotate("text", x = 15, y = 16, label = "\nLoss trials", size = 3.5, color = "#333333") +
  theme(
    text = element_text(size = 12),
    plot.margin = unit(c(0, 0, 0, 0), "cm"),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 10.5),
    legend.position = c(0.875, 0.59),
    legend.title = element_blank()
  )
````
