---
title: "Memory_Encoding_Analysis"
author: "Michael Colwell"
date: "2024-04-05"
output: html_document
---
#Memory encoding task (or 'Hippocampal task') behavioural and neuroimaging data preprocessing analysis scripts for the PEACE Study ('Pitolisant Effects on Affect and Cognition Exploratory Study') (NCT05849675). 

This script includes: 

- Preprocessing of raw behavioural files from the pre-scanner, in-scanner and post-scanner (recognition) tasks
- Main behavioural analysis 
- DDM analysis
- DDM parameter recovery
- DDM posterior predictive checks
- Signal persistence/encoding activity ~ connectivity analysis 
- Signal persistence ~ DDM parameters analysis
- Signal persistence ~ encoding activity lateralisation analysis
- RL parameters ~ DDM parameters analysis

#Rmarkdown script by Michael Colwell (michael.colwell@psych.ox.ac.uk).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library chunk

```{r cars}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggplot2)
library(car)
library(ggbeeswarm)
library(ggrepel)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(sdamr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(sdamr)
library(cowplot)
library(psycho)
library(ggridges)
library(viridis)
library(ggstance)
library(ggdist)
library(gghalves)
library(ggpp)
library(effectsize)
library(lme4)
library(lmerTest)
library(brms)
library(BayesFactor)
library("ggExtra")
library(purrr)
library(broom)
library(moments)
library(gtools)
library(stringr)
library(ggExtra)
```

## Initial Preprocessing (Initial test & Final Test)

```{r pressure, echo=FALSE}
## Set directory; Create list of relevant files; Merge files

# Set working directory

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/Results_Final")

# Create an empty data frame to store the combined data
combined_df <- data.frame()

# Get a list of all .dat files in the directory
dat_files <- list.files(pattern = glob2rx("*com*.log"))

# Loop through each .dat file
for (file in dat_files) {
  # Read the file using readLines()
  lines <- readLines(file)

  # Remove the first three lines
  lines <- lines[-(1:5)]

  # Extract the file name
  file_name <- sub("\\.log$", "", file)

  # Check if the file name contains P001, P002, etc.
  if (grepl("[Pp]\\d{3}", file_name)) {
    # Check if there are lines remaining
    if (length(lines) > 0) {
      # Replace blank spaces with NA in each line
      lines <- lapply(lines, function(line) {
        words <- strsplit(line, "\\s+")[[1]]
        words[words == ""] <- NA
        return(words)
      })

      # Find the maximum number of elements in a line
      max_elements <- max(sapply(lines, length))

      # Create a matrix to store the data
      data_matrix <- matrix(nrow = length(lines), ncol = max_elements)

      # Fill the matrix with the data from the lines
      for (i in seq_along(lines)) {
        row <- lines[[i]]
        data_matrix[i, 1:length(row)] <- row
      }

      # Convert the matrix to a data frame
      df <- as.data.frame(data_matrix, stringsAsFactors = FALSE) # Ensure strings are treated as characters

      # Add a column with the file name to the data frame
      df <- cbind(FileName = file_name, df)

      # Bind the data to the combined data frame
      combined_df <- bind_rows(combined_df, df)
    }
  }
}

# Assign column names
col_names <- c("FileName", "Participant.ID", "Trial", "Event_Type", "Code_Raw", "Time", "TTime", "Uncertainty", "ResponseT", "Uncertainty_2", "ReqTime", "ReqDur", "Stim_Type", "Pair_Index") # Add your column names here

colnames(combined_df) <- col_names

# Prune 'Participant.ID' column to first few letters
combined_df$Participant.ID <- str_sub(combined_df$Participant.ID, 1, 4)

# Convert 'Participant.ID' column to uppercase
combined_df$Participant.ID <- toupper(combined_df$Participant.ID)

# Remove the "FileName" column
combined_df <- combined_df[, !names(combined_df) %in% "FileName"]

combined_df <- combined_df %>%
  filter(Event_Type == "Response")

combined_df$Code <- ifelse(grepl("A", combined_df$Code_Raw), 1,
  ifelse(grepl("L", combined_df$Code_Raw), 2, NA)
)

# Remove the "Code_Raw" column
combined_df <- combined_df[, !names(combined_df) %in% "Code_Raw"]

# Only take the first instance of a button press (Presentation records all inputs) - you may want to change this
combined_df <- combined_df %>%
  distinct(Participant.ID, Trial, .keep_all = TRUE)

# score each trial
combined_df <- combined_df %>%
  mutate(Correct = case_when(
    Trial == "1" & Code == "1" ~ "1",
    Trial == "2" & Code == "1" ~ "1",
    Trial == "3" & Code == "2" ~ "1",
    Trial == "4" & Code == "1" ~ "1",
    Trial == "5" & Code == "1" ~ "1",
    Trial == "6" & Code == "1" ~ "1",
    Trial == "7" & Code == "1" ~ "1",
    Trial == "8" & Code == "1" ~ "1",
    Trial == "9" & Code == "2" ~ "1",
    Trial == "10" & Code == "1" ~ "1",
    Trial == "11" & Code == "2" ~ "1",
    Trial == "12" & Code == "2" ~ "1",
    Trial == "13" & Code == "1" ~ "1",
    Trial == "14" & Code == "1" ~ "1",
    Trial == "15" & Code == "2" ~ "1",
    Trial == "16" & Code == "1" ~ "1",
    Trial == "17" & Code == "1" ~ "1",
    Trial == "18" & Code == "1" ~ "1",
    Trial == "19" & Code == "1" ~ "1",
    Trial == "20" & Code == "1" ~ "1",
    Trial == "21" & Code == "1" ~ "1",
    Trial == "22" & Code == "1" ~ "1",
    Trial == "23" & Code == "2" ~ "1",
    Trial == "24" & Code == "1" ~ "1",
    Trial == "25" & Code == "2" ~ "1",
    Trial == "26" & Code == "1" ~ "1",
    Trial == "27" & Code == "2" ~ "1",
    Trial == "28" & Code == "2" ~ "1",
    Trial == "29" & Code == "1" ~ "1",
    Trial == "30" & Code == "2" ~ "1",
    Trial == "31" & Code == "1" ~ "1",
    Trial == "32" & Code == "1" ~ "1",
    Trial == "33" & Code == "1" ~ "1",
    Trial == "34" & Code == "1" ~ "1",
    Trial == "35" & Code == "1" ~ "1",
    Trial == "36" & Code == "1" ~ "1",
    Trial == "37" & Code == "2" ~ "1",
    Trial == "38" & Code == "1" ~ "1",
    Trial == "39" & Code == "2" ~ "1",
    Trial == "40" & Code == "2" ~ "1",
    Trial == "41" & Code == "2" ~ "1",
    Trial == "42" & Code == "1" ~ "1",
    Trial == "43" & Code == "1" ~ "1",
    Trial == "44" & Code == "1" ~ "1",
    Trial == "45" & Code == "2" ~ "1",
    Trial == "46" & Code == "1" ~ "1",
    Trial == "47" & Code == "1" ~ "1",
    Trial == "48" & Code == "1" ~ "1",
    Trial == "49" & Code == "1" ~ "1",
    Trial == "50" & Code == "1" ~ "1",
    Trial == "51" & Code == "2" ~ "1",
    Trial == "52" & Code == "1" ~ "1",
    Trial == "53" & Code == "1" ~ "1",
    Trial == "54" & Code == "1" ~ "1",
    Trial == "55" & Code == "1" ~ "1",
    Trial == "56" & Code == "1" ~ "1",
    Trial == "57" & Code == "1" ~ "1",
    Trial == "58" & Code == "2" ~ "1",
    Trial == "59" & Code == "1" ~ "1",
    Trial == "60" & Code == "1" ~ "1",
    Trial == "61" & Code == "2" ~ "1",
    Trial == "62" & Code == "1" ~ "1",
    Trial == "63" & Code == "2" ~ "1",
    Trial == "64" & Code == "1" ~ "1",
    Trial == "65" & Code == "1" ~ "1",
    Trial == "66" & Code == "2" ~ "1",
    Trial == "67" & Code == "1" ~ "1",
    Trial == "68" & Code == "1" ~ "1",
    Trial == "69" & Code == "2" ~ "1",
    Trial == "70" & Code == "1" ~ "1",
    Trial == "71" & Code == "1" ~ "1",
    Trial == "72" & Code == "1" ~ "1",
    Trial == "73" & Code == "1" ~ "1",
    Trial == "74" & Code == "2" ~ "1",
    Trial == "75" & Code == "2" ~ "1",
    Trial == "76" & Code == "1" ~ "1",
    Trial == "77" & Code == "1" ~ "1",
    Trial == "78" & Code == "1" ~ "1",
    Trial == "79" & Code == "1" ~ "1",
    Trial == "80" & Code == "2" ~ "1",
    Trial == "81" & Code == "2" ~ "1",
    Trial == "82" & Code == "1" ~ "1",
    Trial == "83" & Code == "1" ~ "1",
    TRUE ~ "0"
  ))

# Images #68 and #48 were corrected in this version of the script, which were previously labelled as distraction stimuli in error.

# Creating a column to sort images into novel (seen in scanner), familiar (seen earlier in day and during scan), and distractors (seen only during final test [not encoded])

combined_df <- combined_df %>%
  mutate(Trial_Type = case_when(
    Code == "2" ~ "Distractor",
    Trial == "10" & Code == "1" ~ "Familiar",
    Trial == "29" & Code == "1" ~ "Familiar",
    Trial == "36" & Code == "1" ~ "Familiar",
    Trial == "48" & Code == "1" ~ "Familiar",
    Trial == "50" & Code == "1" ~ "Familiar",
    Trial == "68" & Code == "1" ~ "Familiar",
    Trial == "78" & Code == "1" ~ "Familiar",
    Trial == "82" & Code == "1" ~ "Familiar",
    TRUE ~ "Novel"
  ))

# Presentation records in tenths of milliseconds -- divide this value by 10 to get standard milliseconds

combined_df$TTime <- as.numeric(combined_df$TTime)
combined_df$Response.time <- combined_df$TTime / 10

# Convert Correctness to numeric
combined_df$Correct <- as.numeric(combined_df$Correct)

# Remove extraneous columns
Cleaned_Memory_Task <- subset(combined_df, select = -c(TTime, Event_Type, Uncertainty, ResponseT, ReqTime, ReqDur, Stim_Type, Pair_Index, Uncertainty_2))

Cleaned_Memory_Task$Code <- recode_factor(Cleaned_Memory_Task$Code, "2" = "Unseen", "1" = "Seen")

# Convert RT for correct responses only

Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  transform(RT_Corr = ifelse(Correct == 1, Response.time, NA))


Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  mutate(Hits = case_when(
    Correct == "1" & Trial_Type == "Novel" ~ "1",
    Correct == "1" & Trial_Type == "Familiar" ~ "1",
    Correct == "0" & Trial_Type == "Novel" ~ "0",
    Correct == "0" & Trial_Type == "Familiar" ~ "0",
    TRUE ~ NA
  ))

Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  mutate(Misses = case_when(
    Correct == "0" & Trial_Type == "Novel" ~ "1",
    Correct == "0" & Trial_Type == "Familiar" ~ "1",
    Correct == "1" & Trial_Type == "Novel" ~ "0",
    Correct == "1" & Trial_Type == "Familiar" ~ "0",
    TRUE ~ NA
  ))

Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  mutate(FAs = case_when(
    Correct == "1" & Trial_Type == "Distractor" ~ "0",
    Correct == "0" & Trial_Type == "Distractor" ~ "1",
    TRUE ~ NA
  ))

Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  mutate(CRs = case_when(
    Correct == "0" & Trial_Type == "Distractor" ~ "0",
    Correct == "1" & Trial_Type == "Distractor" ~ "1",
    TRUE ~ NA
  ))
```
```{r pressure, echo=FALSE}
# DDM Preprocessing Block (Optional)

Cleaned_Memory_Task$rt <- Cleaned_Memory_Task$Response.time * 0.001

DDM <- Cleaned_Memory_Task

DDM <- Cleaned_Memory_Task

DDM <- DDM %>%
  mutate(stim = case_when(
    Code == "Seen" ~ "1",
    Code == "Unseen" ~ "0",
    TRUE ~ NA
  ))

DDM$correct <- DDM$Correct

DDM$subj_idx <- DDM$Participant.ID

DDM <- DDM %>%
  mutate(response = case_when(
    Correct == "1" & stim == "1" ~ "1",
    Correct == "0" & stim == "1" ~ "0",
    Correct == "1" & stim == "0" ~ "0",
    Correct == "0" & stim == "0" ~ "1",
    TRUE ~ NA
  ))

DDM <- DDM %>% select(rt, response, subj_idx, correct, stim)

write.csv(DDM, "C:/Users/micha/Desktop/Memory_Task_DDM.csv", row.names = TRUE)
```






```{r pressure, echo=FALSE}
# Create summary file

Cleaned_Memory_Task <- Cleaned_Memory_Task %>%
  mutate(
    Hits = as.numeric(Hits),
    FAs = as.numeric(FAs),
    Misses = as.numeric(Misses),
    CRs = as.numeric(CRs),
    Correct = as.numeric(Correct),
    RT_Corr = as.numeric(RT_Corr),
    Response.time = as.numeric(Response.time)
  )

M_Encoding_Summary <- Cleaned_Memory_Task %>%
  group_by(Participant.ID, Trial_Type, Code) %>%
  summarize(
    Accuracy = sum(Correct, na.rm = TRUE),
    mean_RT_all = mean(Response.time, na.rm = TRUE),
    mean_RT_corr = mean(RT_Corr, na.rm = TRUE),
    Hits = sum(Hits, na.rm = TRUE),
    FAs = sum(FAs, na.rm = TRUE),
    Misses = sum(Misses, na.rm = TRUE),
    CRs = sum(CRs, na.rm = TRUE)
  )

M_Encoding_Not <- Cleaned_Memory_Task %>%
  group_by(Participant.ID, ) %>%
  summarize(
    Accuracy = sum(Correct, na.rm = TRUE),
    mean_RT_all = mean(Response.time, na.rm = TRUE),
    mean_RT_corr = mean(RT_Corr, na.rm = TRUE),
    Hits = sum(Hits, na.rm = TRUE),
    FAs = sum(FAs, na.rm = TRUE),
    Misses = sum(Misses, na.rm = TRUE),
    CRs = sum(CRs, na.rm = TRUE)
  )

# Convert Accuracy to Accuracy %

# 25 Distractors, #58 Previously Encoded, 8 of which before the scanner.

M_Encoding_Summary$Accuracy_Perc <- ifelse(M_Encoding_Summary$Trial_Type == "Novel",
  M_Encoding_Summary$Accuracy / 50 * 100,
  ifelse(M_Encoding_Summary$Trial_Type == "Familiar",
    M_Encoding_Summary$Accuracy / 8 * 100,
    ifelse(M_Encoding_Summary$Trial_Type == "Distractor",
      M_Encoding_Summary$Accuracy / 25 * 100,
      NA
    )
  )
)
```

```{r pressure, echo=FALSE}
# Quality checks

# Function to detect outliers
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 3.0 * IQR(x) | x > quantile(x, 0.75) + 3.0 * IQR(x))
}

Accuracy_Plot <- ggplot(M_Encoding_Summary, aes(x = as.factor(Trial_Type), y = Accuracy_Perc)) +
  geom_boxplot(outlier.shape = NA) + # Hide outlier points in boxplot
  geom_point(data = M_Encoding_Summary[is_outlier(M_Encoding_Summary$Accuracy_Perc), ], aes(color = Participant.ID)) +
  geom_text_repel(data = M_Encoding_Summary[is_outlier(M_Encoding_Summary$Accuracy_Perc), ], aes(label = Participant.ID), color = "black", size = 3) + # Label outliers
  labs(
    title = "",
    y = "\nRecall Accuracy (%)\n",
    x = "\nTrial Type\n"
  ) +
  theme_minimal() +
  theme(text = element_text(size = 16))

RT_Plot <- ggplot(M_Encoding_Summary, aes(x = as.factor(Trial_Type), y = mean_RT_corr)) +
  geom_boxplot(outlier.shape = NA) + # Hide outlier points in boxplot
  geom_point(data = M_Encoding_Summary[is_outlier(M_Encoding_Summary$mean_RT), ], aes(color = Participant.ID)) +
  geom_text_repel(data = M_Encoding_Summary[is_outlier(M_Encoding_Summary$mean_RT), ], aes(label = Participant.ID), color = "black", size = 3) + # Label outliers
  labs(
    title = "",
    y = "\nResponse Time (ms)\n",
    x = "\nTrial Type\n"
  ) +
  theme_minimal() +
  theme(text = element_text(size = 16))
```

```{r pressure, echo=FALSE}
# Merging/Splitting files further; combining allocation information

ROI_Values <- read.xlsx("C:/Users/micha/Desktop/PEACE_Data_and_Code/ROI_Data/Hip_encoding_sig_clusters_PE.xlsx")

Mem_filtered <- M_Encoding_Summary[grepl("Novel", M_Encoding_Summary$Trial_Type), ]

Mem_filtered_2 <- M_Encoding_Summary[grepl("Familiar", M_Encoding_Summary$Trial_Type), ]

Merged_MemROI <- merge(Mem_filtered, ROI_Values, by = "Participant.ID")
Merged_MemROI_2 <- merge(Mem_filtered_2, ROI_Values, by = "Participant.ID")

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

Merged_MemROI <- merge(Merged_MemROI, Allocation_and_Demographics, by = "Participant.ID")
````



```{r pressure, echo=FALSE}
# Relationship between ROI values and task performance.

# Full_Model_All_PEs

# Create the scatterplot

## PE Boxplots

##

Bil_Hip_Fig <- Merged_MemROI %>% ggplot(aes(x = Allocation, y = Bil_Hipp, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Cluster Mask β\n") +
  xlab("\nBilateral Hippocampus\n") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Basal_forebrain_fig <- Merged_MemROI %>% ggplot(aes(x = Allocation, y = Basal_forebrain, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Cluster Mask β\n") +
  xlab("\nBasal Forebrain\n") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title.y = element_blank(), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Bil_PRC_fig <- Merged_MemROI %>% ggplot(aes(x = Allocation, y = Perirhinal, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Cluster Mask β\n") +
  xlab("\nBilateral PRC\n") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title.y = element_blank(), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Bil_ETH_fig <- Merged_MemROI %>% ggplot(aes(x = Allocation, y = Entorhinal, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Cluster Mask β\n") +
  xlab("\nBilateral ETC\n") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title.y = element_blank(), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))


CombinedPlots <- plot_grid(Bil_Hip_Fig, Basal_forebrain_fig, Bil_PRC_fig, Bil_ETH_fig, align = "h", ncol = 4, labels = c(""))
```



```{r pressure, echo=FALSE}
# Resting state edge strength analysis

# Data merging/clean-up

Edge_MamZ_Hipp <- read.csv("C:/Users/micha/Desktop/PEACE_Data_and_Code/ROI_Data/edge_strengths_Node1_Node2.csv")

# Need to add in Participant.ID column to .csv - NTS.

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

EdgeS_in <- merge(Edge_MamZ_Hipp, Allocation_and_Demographics, by = "Participant.ID")

EdgeS_R <- merge(EdgeS_in, Merged_MemROI_2, by = "Participant.ID")


##########################

# Association between H3R weighted values for edge strengths (resting state) + Hippocampal encoding activity (novel > familiar, significant group cluster)

LM_1 <- lm(Edge.Strengths ~ H3R_Hipp, data = EdgeS_R)

summary(LM_1)

eta_squared(LM_1, ci = 0.95, alternative = "two.sided")

cor.test(EdgeS_R$Edge.Strengths, EdgeS_R$H3R_Hipp)

# Fit regression within each sample
regression_results <- EdgeS_R %>%
  group_by(Allocation) %>%
  group_map(~ tidy(lm(Edge.Strengths ~ H3R_Hipp, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

##########################

# Association between unweighted values for edge strengths (resting state) + Hippocampal encoding activity (novel > familiar, significant group cluster)

LM_2 <- lm(Non.Weight ~ Bil_Hipp, data = EdgeS_R)

summary(LM_2)

eta_squared(LM_2, ci = 0.95, alternative = "two.sided")

cor.test(EdgeS_R$Non.Weight, EdgeS_R$Bil_Hipp)

# Fit regression within each sample
regression_results <- EdgeS_R %>%
  group_by(Allocation) %>%
  group_map(~ tidy(lm(Non.Weight ~ Bil_Hipp, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

##########################

# Figures for publication

# Compute correlation coefficient and p-value
cor_result <- cor.test(EdgeS_R$Edge.Strengths, EdgeS_R$H3R_Hipp)

# Create the scatterplot
Edge_Encoding_Figure <- ggplot(data = EdgeS_R, aes(x = Edge.Strengths, y = H3R_Hipp)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nMammillary Zone ↔ Hippocampus Connectivity\n",
    y = "\nBilateral Hippocampus Activity (Novel > Familiar)\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Edge_Encoding_Figure_Final <- ggMarginal(Edge_Encoding_Figure, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)
```

```{r pressure, echo=FALSE}
# Edge Strengths Figure

# Manually edited it to one * instead of two ** as this is this reflects the TFCE-corrected p-value:

# Node 0 - 1: t = 2.91533; p = 0.9734

Edge_Strengths <- EdgeS_in %>% ggplot(aes(x = Allocation, y = Edge.Strengths, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "*" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Mammillary Zone ↔ Hippocampus Connectivity\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

# Descriptive statistics

EdgeS_in %>%
  group_by(Allocation) %>%
  get_summary_stats(Edge.Strengths, type = "mean_sd")

EdgeS_in %>%
  group_by(Allocation) %>%
  get_summary_stats(Non.Weight, type = "mean_sd")
```




```{r pressure, echo=FALSE}
# Removing excluded data & merging demographics file

# P003, P011, P023, P034, P045, P051, & P059 were excluded from neuroimaging analysis due to technical and adherence issues identified in pre-unblinding data quality checks. The results remain significant with their inclusion.

# During the memory recognition task, the task finished early for P044 due to glitch. For completeness, their data was included and analysed based on percentage correct, however, the findings remain significant with their data excluded from the analysis.

removal_df <- subset(M_Encoding_Summary, Participant.ID != "P003" & Participant.ID != "P007" & Participant.ID != "P011" & Participant.ID != "P034" & Participant.ID != "P045" & Participant.ID != "P059")

M_Encoding_Summary <- droplevels(removal_df)

# Adding demographics file

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics/")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

M_Encoding_Full <- merge(M_Encoding_Summary, Allocation_and_Demographics, by = "Participant.ID")

M_Encoding_Full
```

```{r pressure, echo=FALSE}
# Plots
M_Encoding_Full$Trial_Type <- as.factor(M_Encoding_Full$Trial_Type)

M_Encoding_Full$Trial_Type <- relevel(M_Encoding_Full$Trial_Type, ref = "Novel")

M_Encoding_Seen <- M_Encoding_Full[M_Encoding_Full$Code == "Seen", ]
M_Encoding_Unseen <- M_Encoding_Full[M_Encoding_Full$Code == "Unseen", ]

M_Encoding_Full$Code <- factor(M_Encoding_Full$Code, levels = c("Seen", "Unseen"))

# Overall DF

# In the main paper, significance asterisks were altered to reflect EMM values.

M_Encoding_Full <- M_Encoding_Full %>%
  mutate(Trial_Type = factor(Trial_Type, levels = c("Familiar", "Novel", "Distractor")))

All_acc_Plot <- M_Encoding_Full %>% ggplot(aes(x = Allocation, y = Accuracy_Perc, fill = Allocation)) +
  facet_wrap(~Code) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Recognition accuracy (%)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

# Overall RT

All_RT_Plot <- M_Encoding_Full %>% ggplot(aes(x = Allocation, y = mean_RT_corr, fill = Allocation)) +
  facet_wrap(~Code) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Time to choice (ms)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Combined_plot <- plot_grid(All_acc_Plot, All_RT_Plot, ncol = 1)
```


```{r pressure, echo=FALSE}
# Checking kurtosis values

x <- M_Encoding_Full$Accuracy_Perc

# skewness
skew_val <- skewness(x, na.rm = TRUE)

kurt_val <- kurtosis(x, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)

# numeric vector (your variable of interest)
y <- M_Encoding_Full$mean_RT_all

# skewness
skew_val <- skewness(y, na.rm = TRUE)

kurt_val <- kurtosis(y, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)

# Inferential analyses

# Accuracy analysis

Accuracy_Model <- aov(Accuracy_Perc ~ Allocation + Code + Allocation:Code + Error(Participant.ID), data = M_Encoding_Full)

summary(Accuracy_Model)

###

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Accuracy_Perc ~ Allocation + Code + Allocation:Code + (1 | Participant.ID), data = M_Encoding_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Code)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

M_Encoding_Full %>%
  group_by(Trial_Type, Allocation) %>%
  get_summary_stats(Accuracy_Perc, type = "mean_sd")

# Response time analysis

###

RT_Model <- aov(mean_RT_all ~ Allocation + Code + Allocation:Code + Error(Participant.ID), data = M_Encoding_Full)

summary(RT_Model)

###

RT_Model <- aov(mean_RT_corr ~ Allocation + Code + Allocation:Code + Gender + Digit.Span.Aggregate + Error(Participant.ID), data = M_Encoding_Full)

summary(RT_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(mean_RT_corr ~ Allocation + Code + Allocation:Code + (1 | Participant.ID), data = M_Encoding_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Code)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

M_Encoding_Full %>%
  group_by(Trial_Type, Allocation) %>%
  get_summary_stats(Accuracy_Perc, type = "mean_sd")
```

```{r pressure, echo=FALSE}
# Checking in-scanner engagement

require("knitr")
knitr::opts_knit$set(root.dir = "C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/fmri_engagement/")

##### Set dir first!#########
setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/fmri_engagement/")
#############################

# Create file list
Hipp_Scan_Files <- list.files(pattern = glob2rx("*Hipp*.csv"))

# Attach and detach plyr to avoid library conflicts
library(plyr)

# Merge files based on file list
Hipp_Scan <- do.call(rbind.fill, lapply(Hipp_Scan_Files, function(x) read.csv(x, stringsAsFactors = FALSE)))

detach("package:plyr", unload = TRUE)

# Remove object to save space
rm(Hipp_Scan_Files)

Hipp_Scan_Clean <- Hipp_Scan %>% select(participant, im_type, im_familiarity, trialOrderFile, key_resp2.corr, key_resp2.rt)

Hipp_Scan_Clean <- Hipp_Scan_Clean %>% rename(Participant.ID = participant)

Hipp_Scan_Clean <- Hipp_Scan_Clean %>% drop_na(key_resp2.corr)

library(stringr)

Hipp_Scan_Clean <- Hipp_Scan_Clean %>%
  mutate(Participant.ID = str_replace_all(Participant.ID, "^p", "P") %>% # Convert lowercase 'p' to 'P' at the start
    str_replace("_real", "")) # Remove "_real"

Hipp_Scan_Clean <- Hipp_Scan_Clean %>%
  mutate(trialOrderFile = str_replace_all(trialOrderFile, "scan_order|\\.xlsx", "")) %>%
  rename(Block = trialOrderFile)

Hipp_Scan_Clean <- Hipp_Scan_Clean %>%
  rename(Trial_type = im_familiarity)

Hipp_Scan_Clean <- Hipp_Scan_Clean %>%
  group_by(Participant.ID) %>% # Group by Participant.ID
  mutate(Trial_number = row_number()) %>% # Create sequential trial numbers within each group
  ungroup() # Remove grouping for further operations

Hipp_Scan_Clean <- Hipp_Scan_Clean %>%
  rename(Accuracy = key_resp2.corr)

Hipp_Scan_Summary <- Hipp_Scan_Clean %>%
  group_by(Participant.ID) %>%
  summarise(GoRTmean = mean(key_resp2.rt, na.rm = TRUE), GoRTsd = sd(key_resp2.rt, na.rm = TRUE), AccuratePress_Perc = sum(Accuracy) / 96 * 100, Accuracy_Full = sum(Accuracy))

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Hipp_Scan_Summary_Full <- merge(Hipp_Scan_Summary, Allocation_and_Demographics, by = "Participant.ID")

Hipp_Scan_Clean_Full <- merge(Hipp_Scan_Clean, Allocation_and_Demographics, by = "Participant.ID")
```


```{r pressure, echo=FALSE}
# Analysis of engagement data

Hipp_Scan_Summary_Full$Accuracylog <- log(Hipp_Scan_Summary_Full$Accuracy_Full)

Hipp_Scan_Summary_Full$Participant.ID <- as.factor(Hipp_Scan_Summary_Full$Participant.ID)

# Removal of excluded participants (see note above.)

removal_df <- subset(Hipp_Scan_Summary_Full, Participant.ID != "P003" & Participant.ID != "P007" & Participant.ID != "P011" & Participant.ID != "P034" & Participant.ID != "P045" & Participant.ID != "P059")

Hipp_Scan_Summary_Full <- droplevels(removal_df)

Acc_Plot <- Hipp_Scan_Summary_Full %>% ggplot(aes(x = Allocation, y = AccuratePress_Perc, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Discrimination Accuracy (%)") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Hipp_Scan_Summary_Full$GoRTmean <- (Hipp_Scan_Summary_Full$GoRTmean) * 1000

RT_Plot <- Hipp_Scan_Summary_Full %>% ggplot(aes(x = Allocation, y = GoRTmean, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = " ") +
  ylab("Time to Response (ms)") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

Combined_Plot <- plot_grid(Acc_Plot, RT_Plot)

# numeric vector (your variable of interest)
x <- Hipp_Scan_Summary_Full$AccuratePress_Perc

# skewness
skew_val <- skewness(x, na.rm = TRUE)

kurt_val <- kurtosis(x, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)

# Above skewness/Kurtosis threshold, so log transforming. Retaining the non-log transformed version for visual demonstration (see Methods).

Hipp_Scan_Summary_Full$AccuratePress_Perc_log <- log(Hipp_Scan_Summary_Full$AccuratePress_Perc)

Accuracy_Model <- aov(AccuratePress_Perc_log ~ Allocation + Error(Participant.ID), data = Hipp_Scan_Summary_Full)

summary(Accuracy_Model)

RT_Model <- aov(GoRTmean ~ Allocation + Error(Participant.ID), data = Hipp_Scan_Summary_Full)

summary(RT_Model)
````


```{r pressure, echo=FALSE}
# Checking pre-scanner engagement

## Set directory; Create list of relevant files; Merge files

# Set working directory

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/Results_InitialTest")

# Create an empty data frame to store the combined data
combined_df <- data.frame()

# Get a list of all .dat files in the directory
dat_files <- list.files(pattern = glob2rx("*recpressce*.log"))

# Loop through each .dat file
for (file in dat_files) {
  # Read the file using readLines()
  lines <- readLines(file)

  # Remove the first three lines
  lines <- lines[-(1:5)]

  # Extract the file name
  file_name <- sub("\\.log$", "", file)

  # Check if the file name contains P001, P002, etc.
  if (grepl("[Pp]\\d{3}", file_name)) {
    # Check if there are lines remaining
    if (length(lines) > 0) {
      # Replace blank spaces with NA in each line
      lines <- lapply(lines, function(line) {
        words <- strsplit(line, "\\s+")[[1]]
        words[words == ""] <- NA
        return(words)
      })

      # Find the maximum number of elements in a line
      max_elements <- max(sapply(lines, length))

      # Create a matrix to store the data
      data_matrix <- matrix(nrow = length(lines), ncol = max_elements)

      # Fill the matrix with the data from the lines
      for (i in seq_along(lines)) {
        row <- lines[[i]]
        data_matrix[i, 1:length(row)] <- row
      }

      # Convert the matrix to a data frame
      df <- as.data.frame(data_matrix, stringsAsFactors = FALSE) # Ensure strings are treated as characters

      # Add a column with the file name to the data frame
      df <- cbind(FileName = file_name, df)

      # Bind the data to the combined data frame
      combined_df <- bind_rows(combined_df, df)
    }
  }
}

# Assign column names
col_names <- c("FileName", "Participant.ID", "Trial", "Event_Type", "Code_Raw", "Time", "TTime", "Uncertainty", "ResponseT", "Uncertainty_2", "ReqTime", "ReqDur", "Stim_Type", "Pair_Index") # Add your column names here

colnames(combined_df) <- col_names

# Prune 'Participant.ID' column to first few letters
combined_df$Participant.ID <- str_sub(combined_df$Participant.ID, 1, 4)

# Convert 'Participant.ID' column to uppercase
combined_df$Participant.ID <- toupper(combined_df$Participant.ID)

# Remove the "FileName" column
combined_df <- combined_df[, !names(combined_df) %in% "FileName"]

combined_df <- combined_df %>%
  filter(Event_Type == "Response")

combined_df$Code <- ifelse(grepl("A", combined_df$Code_Raw), 1,
  ifelse(grepl("L", combined_df$Code_Raw), 2, NA)
)

# Remove the "Code_Raw" column
combined_df <- combined_df[, !names(combined_df) %in% "Code_Raw"]

# Only take the first instance of a button press (Presentation records all inputs) - you may want to change this
combined_df <- combined_df %>%
  distinct(Participant.ID, Trial, .keep_all = TRUE)

combined_df <- combined_df %>%
  mutate(Correct = case_when(
    Trial == "1" & Code == "2" ~ "1",
    Trial == "2" & Code == "1" ~ "1",
    Trial == "3" & Code == "2" ~ "1",
    Trial == "4" & Code == "1" ~ "1",
    Trial == "5" & Code == "1" ~ "1",
    Trial == "6" & Code == "2" ~ "1",
    Trial == "7" & Code == "2" ~ "1",
    Trial == "8" & Code == "2" ~ "1",
    Trial == "9" & Code == "1" ~ "1",
    Trial == "10" & Code == "1" ~ "1",
    Trial == "11" & Code == "2" ~ "1",
    Trial == "12" & Code == "1" ~ "1",
    Trial == "13" & Code == "1" ~ "1",
    Trial == "14" & Code == "2" ~ "1",
    Trial == "15" & Code == "1" ~ "1",
    Trial == "16" & Code == "2" ~ "1",
    TRUE ~ "0"
  ))

combined_df$Correct <- as.numeric(combined_df$Correct)

Hipp_PreScan_Summary <- combined_df %>%
  group_by(Participant.ID) %>%
  summarise(AccuratePress_Perc = sum(Correct) / 16 * 100)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Hipp_PreScan_Summary_Full <- merge(Hipp_PreScan_Summary, Allocation_and_Demographics, by = "Participant.ID")
````

```{r pressure, echo=FALSE}
# Analysis of engagement data

Hipp_PreScan_Summary_Full$Participant.ID <- as.factor(Hipp_PreScan_Summary_Full$Participant.ID)

removal_df <- subset(Hipp_PreScan_Summary_Full, Participant.ID != "P003" & Participant.ID != "P007" & Participant.ID != "P011" & Participant.ID != "P034" & Participant.ID != "P045" & Participant.ID != "P059" & Participant.ID != "P021" & Participant.ID != "P022")

Hipp_PreScan_Summary_Full <- droplevels(removal_df)

# Participants who were excluded from the fMRI analysis were excluded from this analysis. P021 and P022 self-reported misunderstanding initial task engagement tasks; their data was not included at this stage. Results remain non-significant with or without their inclusion.

Hipp_PreScan_Summary_Full <- droplevels(removal_df)

Accuracy_Model <- aov(AccuratePress_Perc ~ Allocation + Error(Participant.ID), data = Hipp_PreScan_Summary_Full)

summary(Accuracy_Model)

Hipp_PreScan_Summary_Full %>%
  get_summary_stats(AccuratePress_Perc, type = "mean_sd")
````


```{r pressure, echo=FALSE}
# Signal persistence / FIR analysis

# Importing FIR parameter estimate values and cleaning data

Decay_df <- read.xlsx("C:/Users/micha/Desktop/PEACE_Data_and_Code/ROI_Data/Decay_PEs.xlsx")

Decay_df_long_novel <- Decay_df %>%
  pivot_longer(
    cols = starts_with("Novel_"),
    names_to = "Time",
    values_to = "PEs"
  )

Decay_df_long_novel <- Decay_df_long_novel %>%
  mutate(Time = sub("Novel_B_T", "", Time))

Decay_df_long_novel <- Decay_df_long_novel %>%
  mutate(Time = dplyr::recode(as.character(Time),
    "Novel_R_T1" = "26",
    "Novel_R_T2" = "27",
    "Novel_R_T3" = "28",
    "Novel_R_T4" = "29",
    "Novel_R_T5" = "30",
    "Novel_R_T6" = "31",
    "Novel_R_T7" = "32",
    "Novel_R_T8" = "33",
    "Novel_R_T9" = "34",
    "Novel_R_T10" = "35",
    "Novel_R_T11" = "36",
    "Novel_R_T12" = "37",
    "Novel_R_T13" = "38",
    "Novel_R_T14" = "39",
    "Novel_R_T15" = "40"
  ))

Decay_df_long_familiar <- Decay_df %>%
  pivot_longer(
    cols = starts_with("Fam"),
    names_to = "Time",
    values_to = "PEs"
  )

Decay_df_long_familiar <- Decay_df_long_familiar %>%
  mutate(Time = sub("Familiar_B_T", "", Time))

Decay_df_long_familiar <- Decay_df_long_familiar %>%
  mutate(Time = dplyr::recode(as.character(Time),
    "Familar_R_T1" = "26",
    "Familar_R_T2" = "27",
    "Familar_R_T3" = "28",
    "Familar_R_T4" = "29",
    "Familar_R_T5" = "30",
    "Familar_R_T6" = "31",
    "Familar_R_T7" = "32",
    "Familar_R_T8" = "33",
    "Familar_R_T9" = "34",
    "Familar_R_T10" = "35",
    "Familar_R_T11" = "36",
    "Familar_R_T12" = "37",
    "Familar_R_T13" = "38",
    "Familar_R_T14" = "39",
    "Familar_R_T15" = "40"
  ))

Decay_df_long_novel$Trial_Type <- "Novel"

Decay_df_long_familiar$Trial_Type <- "Familiar"

Decay_df_long_novel_sim <- Decay_df_long_novel %>%
  select(Participant.ID, Time, Trial_Type, PEs)

Decay_df_long_familiar_sim <- Decay_df_long_familiar %>%
  select(Participant.ID, Time, Trial_Type, PEs)

# Rename PEs columns before cbind
Decay_df_long_novel_sim <- Decay_df_long_novel_sim %>% rename(PEs_novel = PEs)
Decay_df_long_familiar_sim <- Decay_df_long_familiar_sim %>% rename(PEs_familiar = PEs)

# Now bind them side-by-side
merged_df <- cbind(Decay_df_long_novel_sim, PEs_familiar = Decay_df_long_familiar_sim$PEs_familiar)

# Subtract safely
merged_df$PE_diff <- merged_df$PEs_novel - merged_df$PEs_familiar

combined_decay_df <- bind_rows(Decay_df_long_novel_sim, Decay_df_long_familiar_sim)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

combined_decay_df <- merge(combined_decay_df, Allocation_and_Demographics, by = "Participant.ID")

merged_df <- merge(merged_df, Allocation_and_Demographics, by = "Participant.ID")
````

```{r pressure, echo=FALSE}
# FIR Analysis Figure (Main manuscript, Fig 2F-I)

merged_df <- merged_df %>%
  filter(as.numeric(Time) >= 26)

merged_df <- merged_df %>%
  mutate(Time = dplyr::recode(as.character(Time),
    "26" = "1",
    "27" = "2",
    "28" = "3",
    "29" = "4",
    "30" = "5",
    "31" = "6",
    "32" = "7",
    "33" = "8",
    "34" = "9",
    "35" = "10",
    "36" = "11",
    "37" = "12",
    "38" = "13",
    "39" = "14",
    "40" = "15"
  ))
avg_df <- merged_df %>%
  group_by(Time, Allocation) %>%
  summarise(PEs_novel = mean(PEs_novel, na.rm = TRUE), PEs_familiar = mean(PEs_familiar, na.rm = TRUE), .groups = "drop")


merged_df$Time <- factor(merged_df$Time, levels = mixedsort(unique(merged_df$Time)))

####

###

Decay_Beta_Df <- Decay_df %>%
  select(Participant.ID, Decay.Beta, H3R.Decay)

Decay_Full_Df <- merge(Merged_MemROI, Decay_Beta_Df, by = "Participant.ID")

Decay_Full_Df_2 <- merge(Edge_MamZ_Hipp, Decay_Full_Df, by = "Participant.ID")

Decay_Full_Df_3 <- merge(M_Encoding_Not, Decay_Full_Df, by = "Participant.ID")

Decay_Full_Df_4 <- merge(Edge_MamZ_Hipp, Decay_Full_Df_3, by = "Participant.ID")

cor_result <- cor.test(Decay_Full_Df_2$Edge.Strengths, Decay_Full_Df_2$H3R.Decay)

cor_result <- cor.test(Decay_Full_Df_3$H3R.Decay, Decay_Full_Df_3$mean_RT_corr.x)

mean_se <- function(x) {
  m <- mean(x)
  se <- sd(x) / sqrt(length(x))
  return(c(y = m, ymin = m - se, ymax = m + se))
}

merged_df$Time <- as.numeric(as.character(merged_df$Time))

glm_preds$Allocation <- factor(glm_preds$Allocation, levels = c("PLACEBO", "ACTIVE"))

Decay_Full_Df_5_long <- Decay_Full_Df_5 %>%
  pivot_longer(
    cols = matches("^(a|v|t|z_trans)\\.(?:0|1)\\.?$"),
    names_to = c(".value", "Trial_type"),
    names_pattern = "^(.*)\\.(\\d)\\.?$"
  ) %>%
  mutate(Trial_type = factor(Trial_type, levels = c("0", "1")))

# Log transform decision policy in pivot df to maintain consistency

Decay_Full_Df_5_long$a <- log(Decay_Full_Df_5_long$a)

Decay_Full_Df_5_long$Trial_type <- recode_factor(Decay_Full_Df_5_long$Trial_type, "0" = "Unseen", "1" = "Seen")

# Figure 2G generation

Figure.2G <- ggplot(glm_preds, aes(x = Time, y = fit, color = Allocation, fill = Allocation, linetype = Allocation)) +
  geom_ribbon(
    aes(ymin = fit - se, ymax = fit + se),
    fill = "grey70",
    alpha = 0.15,
    colour = NA
  ) +
  geom_line(size = 2.4) +
  scale_color_manual(values = rev(RColorBrewer::brewer.pal(3, "Set2")[1:2])) +
  scale_fill_manual(values = rev(RColorBrewer::brewer.pal(3, "Set2")[1:2])) +
  scale_linetype_manual(values = rev(c("solid", "dashed"))) +
  labs(
    x = "Time (Bins)\n",
    y = "Δ Signal Decay ETC Cluster\n"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 16), # Increase tick text size
    axis.text.y = element_text(size = 16), # Y-axis tick size
    axis.title = element_text(size = 18), # Axis labels
    plot.title = element_text(size = 18, face = "bold")
  )

# Figure 2H generation

cor_result <- cor.test(Decay_Full_Df_4$Edge.Strengths, Decay_Full_Df_4$H3R_Hipp)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Decay_Full_Df_4, aes(x = Edge.Strengths, y = H3R_Hipp)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nΔ Signal Decay ETC Cluster\n",
    y = "\nBilateral Hippocampus β - Novel Memory Encoding\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Figure.2H <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)

# Figure 2I

cor_result <- cor.test(Decay_Full_Df_4$Edge.Strengths, Decay_Full_Df_4$H3R.Decay)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Decay_Full_Df_4, aes(x = Edge.Strengths, y = H3R.Decay)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nMammillary Zone ↔ Hippocampus Connectivity\n",
    y = "\nΔ Signal Decay ETC Cluster\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Figure.2I <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)
```


```{r pressure, echo=FALSE}
# DDM Analysis - Checking relationship between signal persistence and encoding-related activity (lateralised to check specificity).

# Left hemisphere - Entorhinal cortex (encoding)

med.fit <- lm(H3R.Decay ~ H3R_leftento, data = Decay_Full_Df_4)

cor_result <- cor.test(Decay_Full_Df_4$Decay.Beta, Decay_Full_Df_4$H3R_leftento)

summary(med.fit)

# Left hemisphere - Hippocampus  (encoding)

med.fit <- lm(H3R.Decay ~ H3R_lefthipp, data = Decay_Full_Df_4)

summary(med.fit)

cor_result <- cor.test(Decay_Full_Df_4$Decay.Beta, Decay_Full_Df_4$H3R_lefthipp)

## Right hemisphere - Entorhinal cortex (encoding)

med.fit <- lm(H3R.Decay ~ H3R_rightento, data = Decay_Full_Df_4)

cor_result <- cor.test(Decay_Full_Df_4$Decay.Beta, Decay_Full_Df_4$H3R_rightento)

summary(med.fit)

# Left hemisphere - Hippocampus  (encoding)

med.fit <- lm(H3R.Decay ~ H3R_righthipp, data = Decay_Full_Df_4)

summary(med.fit)

cor_result <- cor.test(Decay_Full_Df_4$Decay.Beta, Decay_Full_Df_4$H3R_righthipp)

##########################################################################

# DDM Analysis - Checking relationship between signal persistence and DDM params

# Persistence Analysis - Merging relevant files

###########

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task")

ddm_df <- read.csv("pivoted_traces.csv")

Decay_Full_Df_5 <- merge(ddm_df, Decay_Full_Df, by = "Participant.ID")

Decay_Full_Df_5 <- merge(Decay_Full_Df_5, Allocation_and_Demographics, by = "Participant.ID")


# Arcscin transform non-decision time to maintain consistency across analyses
Decay_Full_Df_5$t.a.0 <- asin(sqrt(Decay_Full_Df_5$t.0.))
Decay_Full_Df_5$t.a.1 <- asin(sqrt(Decay_Full_Df_5$t.1.))

# Log transform decision policy to maintain consistency across DDM analyses
Decay_Full_Df_5$a.0.log <- log(Decay_Full_Df_5$a.0)
Decay_Full_Df_5$a.1.log <- log(Decay_Full_Df_5$a.1)

# Legend: v [drift rate], a [decision policy], t [non-decision time], z_trans [initial choice bias]

# Parameter symbols ending in '.0' refer to distractor trials; '.1' refers to previously encoded trials

############################################

#### Figures for publication

# Figure 3E

# Compute correlation coefficient and p-value
cor_result <- cor.test(Decay_Full_Df_5$v.1., Decay_Full_Df_5$H3R.Decay)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Decay_Full_Df_5, aes(x = v.1., y = H3R.Decay)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nDrift rate (v) - Previously encoded\n",
    y = "\nΔ Signal Decay ETC Cluster\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Figure.3E <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)

# Figure 3F

# Compute correlation coefficient and p-value
cor_result <- cor.test(Decay_Full_Df_5$a.0., Decay_Full_Df_5$H3R.Decay)

# Create the scatterplot
Scatterplot_check2 <- ggplot(data = Decay_Full_Df_5, aes(x = a.0., y = H3R.Decay)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "lightgray", alpha = 0.3) + # Enable CI shading
  labs(
    x = "\nDecision Policy (a) - Unseen distractors\n",
    y = "\nΔ Signal Decay ETC Cluster\n"
  ) +
  annotate("text",
    x = Inf, y = -Inf, hjust = 1, vjust = -0.5, size = 5,
    label = paste(
      "r =", round(cor_result$estimate, 3),
      "\np =", ifelse(cor_result$p.value < 0.001, 0.001, format(cor_result$p.value, scientific = FALSE, digits = 3))
    )
  ) +
  geom_point(size = 3.25, color = "#2E5984", alpha = 0.75) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15)
  )

Figure.3F <- ggMarginal(Scatterplot_check2, type = "density", linetype = "blank", fill = "lightblue", color = "black", alpha = 0.8)

######################################################

# Checking LMs for DDM parameters ~ Signal Decay

# Decision policy

med.fit <- lm(a.0.log ~ Decay.Beta, data = Decay_Full_Df_5)

summary(med.fit)

med.fit <- lm(a.1.log ~ Decay.Beta, data = Decay_Full_Df_5)

summary(med.fit)

# Fit regression within each sample
regression_results <- Decay_Full_Df_5_long %>%
  group_by(Trial_type) %>%
  group_map(~ tidy(lm(a ~ H3R.Decay + Allocation.y, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

# Drift rate

med.fit <- lm(v.0. ~ Decay.Beta, data = Decay_Full_Df_5)

summary(med.fit)

med.fit <- lm(v.1. ~ Decay.Beta, data = Decay_Full_Df_5)

summary(med.fit)

# Fit regression within each sample
regression_results <- Decay_Full_Df_5_long %>%
  group_by(Trial_type) %>%
  group_map(~ tidy(lm(v ~ H3R.Decay + Allocation.y, data = .x)))

# Combine into one data frame
regression_df <- bind_rows(regression_results, .id = "Participant.ID")

# Summarize posterior over betas
beta_summary <- regression_df %>%
  group_by(term) %>%
  summarise(
    mean = mean(estimate),
    lower = quantile(estimate, 0.025),
    upper = quantile(estimate, 0.975)
  )

######################################################
````


```{r pressure, echo=FALSE}
########

### Figures for publication

# Figure 3C

mean_se <- function(x) {
  m <- mean(x)
  se <- sd(x) / sqrt(length(x))
  return(c(y = m, ymin = m - se, ymax = m + se))
}

# Plot to demonstrate LR interaction effect
Interaction_Graph <- ggplot(Decay_Full_Df_5_long, aes(x = Trial_type, y = v, color = Allocation, group = Allocation)) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  # Left side (for 'Loss')
  stat_slab(
    data = subset(Decay_Full_Df_5_long, Trial_type == "Seen"), # Only data where Trial_type is 'Loss'
    side = "left", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = -0.15)
  ) +

  # Right side (for 'Win')
  stat_slab(
    data = subset(Decay_Full_Df_5_long, Trial_type == "Unseen"), # Only data where Trial_type is 'Win'
    side = "right", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = 0.15)
  ) +
  geom_line(aes(group = Participant.ID), linetype = "dashed", size = 0.175, alpha = 0.38) +

  # Points and lines (jittered and connected by Participant.ID)
  geom_point(position = position_jitternudge(
    jitter.width = 0.2, jitter.height = -0.3, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.15, alpha = 0.55) +

  # Lines connecting points for each Participant.ID (grouping)

  # Labels and title
  labs(
    title = "",
    x = "",
    y = "\nDrift Rate (v)\n"
  ) +
  theme_minimal() +
  scale_shape_manual(values = c(19, 15)) + # Custom shape for Allocation

  # Confidence ribbon (mean ± SE)
  stat_summary(
    fun.data = mean_se,
    geom = "ribbon",
    aes(group = Allocation),
    fill = "grey70", # or "lightgrey", "#CCCCCC", etc.
    alpha = 0.25,
    colour = NA # removes border
  ) +

  # Group mean line
  stat_summary(
    fun = mean,
    geom = "line",
    aes(group = Allocation, color = Allocation),
    size = 1.9
  )

# Figure 3D

# Plot to demonstrate LR interaction effect
Interaction_Graph <- ggplot(Decay_Full_Df_5_long, aes(x = Trial_type, y = a, color = Allocation, group = Allocation)) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  # Left side (for 'Loss')
  stat_slab(
    data = subset(Decay_Full_Df_5_long, Trial_type == "Seen"), # Only data where Trial_type is 'Loss'
    side = "left", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = -0.15)
  ) +

  # Right side (for 'Win')
  stat_slab(
    data = subset(Decay_Full_Df_5_long, Trial_type == "Unseen"), # Only data where Trial_type is 'Win'
    side = "right", scale = 0.5, show.legend = F, alpha = 0.5,
    aes(fill = Allocation), # Color the slabs based on 'Allocation'
    .width = c(.50, .95, 1), linetype = "blank", position = position_nudge(x = 0.15)
  ) +
  geom_line(aes(group = Participant.ID), linetype = "dashed", size = 0.175, alpha = 0.36) +

  # Points and lines (jittered and connected by Participant.ID)
  geom_point(position = position_jitternudge(
    jitter.width = 0.2, jitter.height = -0.3, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.15, alpha = 0.55) +

  # Lines connecting points for each Participant.ID (grouping)

  # Labels and title
  labs(
    title = "",
    x = "",
    y = "\nLog Decision Policy (a)\n"
  ) +
  theme_minimal() +
  scale_shape_manual(values = c(19, 15)) + # Custom shape for Allocation

  # Confidence ribbon (mean ± SE)
  stat_summary(
    fun.data = mean_se,
    geom = "ribbon",
    aes(group = Allocation),
    fill = "grey70", # or "lightgrey", "#CCCCCC", etc.
    alpha = 0.2,
    colour = NA # removes border
  ) +

  # Group mean line
  stat_summary(
    fun = mean,
    geom = "line",
    aes(group = Allocation, color = Allocation),
    size = 1.9
  )

###

# Non-decision time plot (Supplementary Mats.)

Ter_plot <- Decay_Full_Df_5_long %>% ggplot(aes(x = Allocation.y, y = t, fill = Allocation.y)) +
  facet_wrap(~Trial_type) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Non-decision time (Ter)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation.y, shape = Allocation.y), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))


Decay_Full_Df_5_long <- Decay_Full_Df_5 %>%
  pivot_longer(
    cols = c(z_trans.0., z_trans.1.),
    names_to = "Trial_type",
    names_prefix = "z",
    values_to = "z"
  )

# Initial choice bias plot (Supplementary Mats.)

bias_plot <- Decay_Full_Df_5_long %>% ggplot(aes(x = Allocation.y, y = z_trans, fill = Allocation.y)) +
  facet_wrap(~Trial_type) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Initial Choice Bias (z)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation.y, shape = Allocation.y), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

# Inter-trial variability in non-decision time plot (Supplementary Mats.)

st_plot <- Decay_Full_Df_5 %>% ggplot(aes(x = Allocation.y, y = st, fill = Allocation.y)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Inter-trial variability - non-decision time (st)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation.y, shape = Allocation.y), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

# Inter-trial variability in initial choice bias plot (Supplementary Mats.)

sz_plot <- Decay_Full_Df_5 %>% ggplot(aes(x = Allocation.y, y = sz, fill = Allocation.y)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "holm",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Inter-trial variability - initial choice bias (sz)\n") +
  xlab("") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation.y, shape = Allocation.y), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))
````

```{r pressure, echo=FALSE}
# Inferential analysis - DDM across allocation groups

# Non-decision time

ANCOVA_Drift <- aov(t ~ Allocation.y * Trial_type + Error(Participant.ID), data = Decay_Full_Df_5_long)

summary(ANCOVA_Drift)

# Initial choice bias

ANCOVA_Drift <- aov(z_trans ~ Allocation.y * Trial_type + Error(Participant.ID), data = Decay_Full_Df_5_long)

summary(ANCOVA_Drift)

# Decision policy

ANCOVA_Drift <- aov(a ~ Allocation.y * Trial_type + Error(Participant.ID), data = Decay_Full_Df_5_long)

summary(ANCOVA_Drift)

# Significant

model_linear <- lmer(a ~ Allocation.y + Trial_type + Allocation.y:Trial_type + (1 | Participant.ID), data = Decay_Full_Df_5_long)

summary(model_linear)

anova(model_linear, type = 2) # Type III ANOVA-like table

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation.y | Trial_type)

confint(model_linear, method = "Wald")

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

#######

ANCOVA_Drift <- aov(v ~ Allocation.y * Trial_type + Error(Participant.ID), data = Decay_Full_Df_5_long)

summary(ANCOVA_Drift)

# Significant

model_linear <- lmer(v ~ Allocation.y + Trial_type + Allocation.y:Trial_type + (1 | Participant.ID), data = Decay_Full_Df_5_long)

summary(model_linear)

anova(model_linear, type = 2) # Type III ANOVA-like table

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation.y | Trial_type)

confint(model_linear, method = "Wald")

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)
````

```{r pressure, echo=FALSE}
# DDM Param recovery

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/DDM/")

MasterDDM_sim <- read.csv("Param_recovery.csv", header = TRUE, stringsAsFactors = FALSE)

MasterDDM_sim$Blank <- "Blank"

BoundarySep <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = log(a.0.), fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Log boundary separation (a)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = log(1.5), linetype = "dashed", color = "orange", size = 1)

DriftRate <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = v.0., fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Drift rate (v)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "orange", size = 1) +
  ylim(NA, 2.9)

Dec <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = asin(sqrt(MasterDDM_sim$t.0.)), fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Non-decision time (Ter)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = asin(sqrt(0.15)), linetype = "dashed", color = "orange", size = 1)

Non_Bias <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = z_trans.0., fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Initial Choice Bias (z)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.6681878, linetype = "dashed", color = "orange", size = 1)

var_v <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = sz, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Inter-trial bias variability (sz)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "orange", size = 1)

var_ter <- MasterDDM_sim %>% ggplot(aes(x = Blank, y = st, fill = Blank)) +
  stat_slab(
    side = "right", scale = 0.5, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  scale_color_manual(values = c("#828283")) +
  scale_fill_manual(values = c("#828283")) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  labs(title = " ") +
  ylab("Inter-trial non-decision time variability (st)") +
  xlab("") +
  theme_minimal() +
  theme(legend.position = "none", text = element_text(size = 14), axis.title.y = element_text(size = 17), strip.text = element_blank(), axis.text.x = element_blank()) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(
    position = position_jitternudge(
      jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
    ), aes(color = Blank, shape = Blank),
    size = 4.4, stroke = 0.2, alpha = 0.5
  ) +
  scale_shape_manual(values = c(19, 15)) +
  geom_hline(yintercept = 0.2, linetype = "dashed", color = "orange", size = 1)

CombinedPlots2 <- plot_grid(BoundarySep, DriftRate, Dec, Non_Bias, var_v, var_ter, labels = c(""), label_size = 20)
````

```{r pressure, echo=FALSE}
## Posterior predictive checks

setwd("C:/Users/micha/Desktop/Histamine_Learning_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/DDM")

# Load and clean
real_data <- read_csv("Memory_Task_DDM.csv")
sim_data <- read_csv("posterior_predictive_simulation.csv")

# Label
real_data$Data_Type <- "Real"
sim_data$Data_Type <- "Simulated"

# Fix types
real_data <- real_data %>%
  mutate(
    correct = as.numeric(response == stim),
    rt = as.numeric(rt),
    stim = as.numeric(stim)
  )

sim_data <- sim_data %>%
  mutate(
    correct = as.numeric(correct),
    rt = as.numeric(rt),
    stim = as.numeric(stim)
  )

# Combine
all_data <- bind_rows(real_data, sim_data)

# Summarise per subject + stim
summary_data <- all_data %>%
  group_by(subj_idx, stim, Data_Type) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    accuracy = mean(correct, na.rm = TRUE),
    .groups = "drop"
  )

# Plot
one <- ggplot(summary_data, aes(x = mean_rt, fill = Data_Type, linetype = Data_Type)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~stim) +
  xlab("\nTime to Choice (ms)\n") +
  ylab("\nP(Density)\n") +
  theme(legend.position = "none", text = element_text(size = 14), axis.title = element_text(size = 16)) +
  theme_minimal()


two <- ggplot(summary_data, aes(x = accuracy, fill = Data_Type, linetype = Data_Type)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~stim) +
  xlab("\nOverall Accuracy\n") +
  ylab("\nP(Density)\n") +
  theme(legend.position = "none", text = element_text(size = 14), axis.title = element_text(size = 16)) +
  theme_minimal()

combined <- plot_grid(one, two, cols = 1)
````
```{r b0, echo=FALSE, include=TRUE}
# Metachecks - checking RL task parameters and relationship with DDM parameters (see Supplementary Note 8, final paragraph).

setwd("C:/Users/micha/Desktop/Histamine_Learning_Data_and_Code/Behavioural_Data/Memory_Encoding_Task/DDM")

# Load and clean
RL_ddm <- read_csv("Meta_DDM_3.csv")

collapsed_df <- RL_ddm %>%
  group_by(Participant.ID) %>%
  summarise(across(c(LR_recipmodel, inv_recipmodel, Excl_LR, Excl_Inv), mean, na.rm = TRUE))

n_back_ddm <- read_csv("Meta_DDM_2.csv")

memory_ddm <- read_csv("Meta_DDM_1.csv")

Merged_1 <- merge(collapsed_df, n_back_ddm, by = "Participant.ID")
Merged_DDM_Meta <- merge(Merged_1, memory_ddm, by = "Participant.ID")

win_df <- RL_ddm %>%
  filter(Trial_type == "Win") %>%
  group_by(Participant.ID) %>%
  summarise(across(c(LR_recipmodel, inv_recipmodel, Excl_LR, Excl_Inv), mean, na.rm = TRUE))

loss_df <- RL_ddm %>%
  filter(Trial_type == "Loss") %>%
  group_by(Participant.ID) %>%
  summarise(across(c(LR_recipmodel, inv_recipmodel, Excl_LR, Excl_Inv), mean, na.rm = TRUE))

Merged_1 <- merge(win_df, n_back_ddm, by = "Participant.ID")
Merged_2 <- merge(loss_df, Merged_1, by = "Participant.ID")
Merged_DDM_Meta <- merge(Merged_2, memory_ddm, by = "Participant.ID")

## LM analysis - working memory params

# Win trials - LR ~ working memory DDM

med.fit <- lm(LR_recipmodel.x ~ v_ddm, data = Merged_DDM_Meta)

summary(med.fit)

# Win trials - inv. decision temp ~ working memory drift rate

med.fit <- lm(inv_recipmodel.x ~ v_ddm, data = Merged_DDM_Meta)

summary(med.fit)

###

# Loss trials - LR ~ working memory ddm

med.fit <- lm(LR_recipmodel.y ~ v_ddm, data = Merged_DDM_Meta)

summary(med.fit)

# Loss trials - inv. decision temp ~ working memory ddm

med.fit <- lm(inv_recipmodel.y ~ v_ddm, data = Merged_DDM_Meta)

summary(med.fit)

####################

## LM analysis - memory recognition drift rate

#Average v across unseen and distractor conditions to simplify analysis

Merged_DDM_Meta$avg_v <- (Merged_DDM_Meta$`v(0)` + Merged_DDM_Meta$`v(1)`) / 2

# Win trials - LR ~ v

med.fit <- lm(LR_recipmodel.x ~ avg_v, data = Merged_DDM_Meta)

summary(med.fit)

# Win trials - inv. decision temp ~  v

med.fit <- lm(inv_recipmodel.x ~ avg_v, data = Merged_DDM_Meta)

summary(med.fit)

####

# Loss trials - LR ~ v

med.fit <- lm(LR_recipmodel.y ~ avg_v, data = Merged_DDM_Meta)

summary(med.fit)

# Loss trials - inv. decision temp ~  v

med.fit <- lm(inv_recipmodel.y ~ avg_v, data = Merged_DDM_Meta)

summary(med.fit)


##################################################################
````
