---
title: "Questionnaire_Analysis"
author: "Michael Colwell"
date: "2024-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis script for Questionnaire data (PEACE Study), by Michael Colwell (michael.colwell@psych.ox.ac.uk / michaelcolwell92@gmail.com)

These scripts analyse questionnaire data collected on the day of drug or placebo administration.

Most of these data have two relevant time-points -- before administration of the drug/placebo (pre) and four hours post-administration (post). The subjective cognition questionnaire
was collected at four timepoints.

If you have any questions about this script, please feel free to email the author.

```{r cars}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggplot2)
library(car)
library(ggbeeswarm)
library(ggrepel)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(sdamr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(sdamr)
library(cowplot)
library(psycho)
library(ggridges)
library(viridis)
library(ggstance)
library(ggdist)
library(gghalves)
library(ggpp)
library(effectsize)
library(lme4)
library(lmerTest)
library(fmsb)
```

## Initial cleaning and combination with allocation/demographics information.

```{r pressure, echo=FALSE}
setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Questionnaires/")

Questionnaires_df <- read.csv("PEACE_Study_Questionnaires_Combined.csv")

# Participant data for P049 at baseline is missing -- presumed issue with data collection software. Omitted from analysis. Data for participant P059 is also removed due to data quality
# and compliance concerns -- results do not meaningfully changes with or without their inclusion.

removal_df <- subset(Questionnaires_df, Participant.ID != "P049")

Questionnaires_df <- droplevels(removal_df)

# Add in demographics information

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

Questionnaires_df_master <- merge(Questionnaires_df, Allocation_and_Demographics, by = "Participant.ID")

Questionnaires_df_master_post <- Questionnaires_df_master %>% filter(!str_detect(PRE.POST, "PRE"))
Questionnaires_df_master_pre <- Questionnaires_df_master %>% filter(!str_detect(PRE.POST, "POST"))

## Load in subjective cognition df

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Questionnaires/")

SUBCOG_df <- read.csv("Subjective_Cognition_Combined.csv")

# Participant P049 was removed due to missing baseline data values

removal_df <- subset(SUBCOG_df, Participant.ID != "P049")

SUBCOG_df <- droplevels(removal_df)

SUBCOG_df_master <- merge(SUBCOG_df, Allocation_and_Demographics, by = "Participant.ID")
```


```{r pressure, echo=FALSE}
# Final data parsing before analysis -- splitting the data to prepare for baseline-adjusted ANCOVA analysis.

# Side effects analysis

# Note that we will not include the items for 'sexual side effects' and 'insomnia' in the write-up due to the acute nature of the experimental design.

ANCOdf1 <- Questionnaires_df_master_post[c("Allocation", "Participant.ID", "Appetite.decreased.SE", "Appetite.increased.SE", "Drowsiness.fatigue.SE", "Insomnia.SE", "Sexual.side.effects.SE", "Sweating.SE", "Tremors.SE", "Agitation.SE", "Anxiety.Nervousness.SE", "Diarrhoea.SE", "Dry.mouth.SE", "Indigestion.SE", "Nausea.SE", "Upset.stomach", "SE.Total")]

ANCOdf1 <- rename(ANCOdf1, Appetite.decreased.SE.Post = Appetite.decreased.SE)
ANCOdf1 <- rename(ANCOdf1, Appetite.increased.SE.Post = Appetite.increased.SE)
ANCOdf1 <- rename(ANCOdf1, Drowsiness.fatigue.SE.Post = Drowsiness.fatigue.SE)
ANCOdf1 <- rename(ANCOdf1, Insomnia.SE.Post = Insomnia.SE)
ANCOdf1 <- rename(ANCOdf1, Sexual.side.effects.SE.Post = Sexual.side.effects.SE)
ANCOdf1 <- rename(ANCOdf1, Sweating.SE.Post = Sweating.SE)
ANCOdf1 <- rename(ANCOdf1, Tremors.SE.Post = Tremors.SE)
ANCOdf1 <- rename(ANCOdf1, Agitation.SE.Post = Agitation.SE)
ANCOdf1 <- rename(ANCOdf1, Anxiety.Nervousness.SE.Post = Anxiety.Nervousness.SE)
ANCOdf1 <- rename(ANCOdf1, Diarrhoea.SE.Post = Diarrhoea.SE)
ANCOdf1 <- rename(ANCOdf1, Dry.mouth.SE.Post = Dry.mouth.SE)
ANCOdf1 <- rename(ANCOdf1, Indigestion.SE.Post = Indigestion.SE)
ANCOdf1 <- rename(ANCOdf1, Nausea.SE.Post = Nausea.SE)
ANCOdf1 <- rename(ANCOdf1, Upset.stomach.Post = Upset.stomach)
ANCOdf1 <- rename(ANCOdf1, SE.Total.Post = SE.Total)


ANCOdf2 <- Questionnaires_df_master_pre[c("Allocation", "Participant.ID", "Appetite.decreased.SE", "Appetite.increased.SE", "Drowsiness.fatigue.SE", "Insomnia.SE", "Sexual.side.effects.SE", "Sweating.SE", "Tremors.SE", "Agitation.SE", "Anxiety.Nervousness.SE", "Diarrhoea.SE", "Dry.mouth.SE", "Indigestion.SE", "Nausea.SE", "Upset.stomach", "SE.Total")]

ANCOdf2 <- rename(ANCOdf2, Appetite.decreased.SE.Pre = Appetite.decreased.SE)
ANCOdf2 <- rename(ANCOdf2, Appetite.increased.SE.Pre = Appetite.increased.SE)
ANCOdf2 <- rename(ANCOdf2, Drowsiness.fatigue.SE.Pre = Drowsiness.fatigue.SE)
ANCOdf2 <- rename(ANCOdf2, Insomnia.SE.Pre = Insomnia.SE)
ANCOdf2 <- rename(ANCOdf2, Sexual.side.effects.SE.Pre = Sexual.side.effects.SE)
ANCOdf2 <- rename(ANCOdf2, Sweating.SE.Pre = Sweating.SE)
ANCOdf2 <- rename(ANCOdf2, Tremors.SE.Pre = Tremors.SE)
ANCOdf2 <- rename(ANCOdf2, Agitation.SE.Pre = Agitation.SE)
ANCOdf2 <- rename(ANCOdf2, Anxiety.Nervousness.SE.Pre = Anxiety.Nervousness.SE)
ANCOdf2 <- rename(ANCOdf2, Diarrhoea.SE.Pre = Diarrhoea.SE)
ANCOdf2 <- rename(ANCOdf2, Dry.mouth.SE.Pre = Dry.mouth.SE)
ANCOdf2 <- rename(ANCOdf2, Indigestion.SE.Pre = Indigestion.SE)
ANCOdf2 <- rename(ANCOdf2, Nausea.SE.Pre = Nausea.SE)
ANCOdf2 <- rename(ANCOdf2, Upset.stomach.Pre = Upset.stomach)
ANCOdf2 <- rename(ANCOdf2, SE.Total.Pre = SE.Total)

ANCOdfcomp <- left_join(ANCOdf1, ANCOdf2, by = c("Participant.ID", "Allocation"))

# Baseline-adjusted ANCOVA analysis of main questionnaire data (excluding subjective cognition data)

# Appetite - Decrease

ANCOVA_Appetite_down <- aov(Appetite.decreased.SE.Post ~ Allocation + Appetite.decreased.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Appetite_down)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Appetite.decreased.SE.Post, type = "mean_sd")

# Appetite - Increase

ANCOVA_Appetite_up <- aov(Appetite.increased.SE.Post ~ Allocation + Appetite.increased.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Appetite_up)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Appetite.increased.SE.Pre, type = "mean_sd")

# Drowsiness/Fatigue

ANCOVA_Drowsiness <- aov(Drowsiness.fatigue.SE.Post ~ Allocation + Drowsiness.fatigue.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Drowsiness)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Drowsiness.fatigue.SE.Pre, type = "mean_sd")


# Insomnia - Not reported as did not sample sleeping during the VAS time period.

ANCOVA_Insom <- aov(Insomnia.SE.Post ~ Allocation + Insomnia.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Insom)

# Sexual side effects - Not reported as not appropriate during the VAS time period.

ANCOVA_Se <- aov(Sexual.side.effects.SE.Post ~ Allocation + Sexual.side.effects.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Se)

# Sweating

ANCOVA_Sweat <- aov(Sweating.SE.Post ~ Allocation + Sweating.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Sweat)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Sweating.SE.Post, type = "mean_sd")

# Tremors

ANCOVA_Tremors <- aov(Tremors.SE.Post ~ Allocation + Tremors.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Tremors)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Tremors.SE.Post, type = "mean_sd")

# Agitation

ANCOVA_Ag <- aov(Agitation.SE.Post ~ Allocation + Agitation.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Ag) # Score for for pre is '0' so automatically ejected from the model.

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Agitation.SE.Post, type = "mean_sd")

# Anxiety.Nervousness

ANCOVA_Anx_Nervous <- aov(Anxiety.Nervousness.SE.Post ~ Allocation + Anxiety.Nervousness.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Anx_Nervous)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Anxiety.Nervousness.SE.Post, type = "mean_sd")

# Diarrhea

ANCOVA_Diar <- aov(Diarrhoea.SE.Post ~ Allocation + Diarrhoea.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Diar) # Score for for pre is '0' so automatically ejected from the model.

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Diarrhoea.SE.Pre, type = "mean_sd")

# Dry mouth

ANCOVA_Dry_Mouth <- aov(Dry.mouth.SE.Post ~ Allocation + Dry.mouth.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Dry_Mouth)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Dry.mouth.SE.Post, type = "mean_sd")

# Indigestion

ANCOVA_Indigestion <- aov(Indigestion.SE.Post ~ Allocation + Indigestion.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Indigestion)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Indigestion.SE.Post, type = "mean_sd")

# Nausea

ANCOVA_Nausea <- aov(Nausea.SE.Post ~ Allocation + Nausea.SE.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_Nausea)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Nausea.SE.Post, type = "mean_sd")

# Upset.stomach

ANCOVA_UpsStom <- aov(Upset.stomach.Post ~ Allocation + Upset.stomach.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_UpsStom)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(Upset.stomach.Post, type = "mean_sd")

# Side effects overall

ANCOVA_SE_overall <- aov(SE.Total.Post ~ Allocation + SE.Total.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_SE_overall)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(SE.Total.Post, type = "mean_sd")

#####
```
```{r pressure, echo=FALSE}
# Side effects figure(s)
# Ap - Down

Questionnaires_df_master_post$Appetite.decreased.SE <- as.factor(Questionnaires_df_master_post$Appetite.decreased.SE)

frequency_table <- Questionnaires_df_master_post %>%
  count(Allocation, Appetite.decreased.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

App_Down <- frequency_table %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Appetite.decreased.SE)) +
  geom_col() +
  labs(x = " ", y = "Decreased appetite\n") +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Ap - Up

Questionnaires_df_master_post$Appetite.increased.SE <- as.factor(Questionnaires_df_master_post$Appetite.increased.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Appetite.increased.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

App_Up <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Appetite.increased.SE)) +
  geom_col() +
  labs(x = " ", y = "Increased appetite\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Drowsiness.Fatigue

Questionnaires_df_master_post$Drowsiness.fatigue.SE <- as.factor(Questionnaires_df_master_post$Drowsiness.fatigue.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Drowsiness.fatigue.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Drowsiness.fatigue <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Drowsiness.fatigue.SE)) +
  geom_col() +
  labs(x = " ", y = "Drowsiness / fatigue\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Sweating

Questionnaires_df_master_post$Sweating.SE <- as.factor(Questionnaires_df_master_post$Sweating.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Sweating.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Sweating <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Sweating.SE)) +
  geom_col() +
  labs(x = " ", y = "Sweating\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Tremors

Questionnaires_df_master_post$Tremors.SE <- as.factor(Questionnaires_df_master_post$Tremors.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Tremors.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Tremors <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Tremors.SE)) +
  geom_col() +
  labs(x = " ", y = "Tremors\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Agitation

Questionnaires_df_master_post$Agitation.SE <- as.factor(Questionnaires_df_master_post$Agitation.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Agitation.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Agit <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Agitation.SE)) +
  geom_col() +
  labs(x = " ", y = "Agitation\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Anxiety.Nervousness

Questionnaires_df_master_post$Anxiety.Nervousness.SE <- as.factor(Questionnaires_df_master_post$Anxiety.Nervousness.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Anxiety.Nervousness.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Anx <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Anxiety.Nervousness.SE)) +
  geom_col() +
  labs(x = " ", y = "Anxiety\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Diarrhoea

Questionnaires_df_master_post$Diarrhoea.SE <- as.factor(Questionnaires_df_master_post$Diarrhoea.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Diarrhoea.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Diarr <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Diarrhoea.SE)) +
  geom_col() +
  labs(x = " ", y = "Diarrhoea\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Dry mouth

Questionnaires_df_master_post$Dry.mouth.SE <- as.factor(Questionnaires_df_master_post$Dry.mouth.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Dry.mouth.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

DryM <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Dry.mouth.SE)) +
  geom_col() +
  labs(x = " ", y = "Dry mouth\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Indigestion

Questionnaires_df_master_post$Indigestion.SE <- as.factor(Questionnaires_df_master_post$Indigestion.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Indigestion.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Indi <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Indigestion.SE)) +
  geom_col() +
  labs(x = " ", y = "Indigestion\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Nausea

Questionnaires_df_master_post$Nausea.SE <- as.factor(Questionnaires_df_master_post$Nausea.SE)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Nausea.SE) %>%
  mutate(percent = n / sum(n) * 100 * 2)

Nausea <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Nausea.SE)) +
  geom_col() +
  labs(x = " ", y = "Nausea\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Upset stomach

Questionnaires_df_master_post$Upset.stomach <- as.factor(Questionnaires_df_master_post$Upset.stomach)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, Upset.stomach) %>%
  mutate(percent = n / sum(n) * 100 * 2)

UpsStom <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = Upset.stomach)) +
  geom_col() +
  labs(x = " ", y = "Upset stomach\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# SE Total

Questionnaires_df_master_post$SE.Total <- as.factor(Questionnaires_df_master_post$SE.Total)

frequency_table_2 <- Questionnaires_df_master_post %>%
  count(Allocation, SE.Total) %>%
  mutate(percent = n / sum(n) * 100 * 2)

SE_Total <- frequency_table_2 %>%
  ggplot(aes(y = fct_rev(Allocation), x = percent, fill = SE.Total)) +
  geom_col() +
  labs(x = " ", y = "Side effects aggregate\n") +
  theme_minimal() +
  scale_fill_manual(
    values = c("0" = "#009e73", "1" = "#f0e442", "2" = "#e69f00", "3" = "#d55e00"),
    labels = c("0" = "Not at all", "1" = "Somewhat", "2" = "Moderately", "3" = "Very much")
  ) +
  theme(axis.text.x = element_blank(), axis.title.y = element_text(size = 12), axis.text.y = element_text(size = 10), legend.position = "none")

# Combine all

CombinedPlots <- plot_grid(Agit, Anx, App_Down, App_Up, Diarr, Drowsiness.fatigue, DryM, Indi, Nausea, Sweating, Tremors, UpsStom, align = "v", nrow = 6, ncol = 2, label_size = 20)
```


```{r pressure, echo=FALSE}
# Final data parsing before analysis -- splitting the data to prepare for baseline-adjusted ANCOVA analysis.

# STAI (state), VAS, PANAS and state hedonia questionnaire analysis

ANCOdf1 <- Questionnaires_df_master_post[c("Allocation", "Participant.ID", "STAI.S.Total", "PANAS.negative", "PANAS.positive", "VAS.negative", "VAS.positive", "DARS.Total")]

ANCOdf1 <- rename(ANCOdf1, STAI.S.Total.Post = STAI.S.Total)
ANCOdf1 <- rename(ANCOdf1, PANAS.negative.Post = PANAS.negative)
ANCOdf1 <- rename(ANCOdf1, PANAS.positive.Post = PANAS.positive)
ANCOdf1 <- rename(ANCOdf1, VAS.negative.Post = VAS.negative)
ANCOdf1 <- rename(ANCOdf1, VAS.positive.Post = VAS.positive)
ANCOdf1 <- rename(ANCOdf1, DARS.Total.Post = DARS.Total)

ANCOdf2 <- Questionnaires_df_master_pre[c("Allocation", "Participant.ID", "STAI.S.Total", "PANAS.negative", "PANAS.positive", "VAS.negative", "VAS.positive", "DARS.Total")]

ANCOdf2 <- rename(ANCOdf2, STAI.S.Total.Pre = STAI.S.Total)
ANCOdf2 <- rename(ANCOdf2, PANAS.negative.Pre = PANAS.negative)
ANCOdf2 <- rename(ANCOdf2, PANAS.positive.Pre = PANAS.positive)
ANCOdf2 <- rename(ANCOdf2, VAS.negative.Pre = VAS.negative)
ANCOdf2 <- rename(ANCOdf2, VAS.positive.Pre = VAS.positive)
ANCOdf2 <- rename(ANCOdf2, DARS.Total.Pre = DARS.Total)

ANCOdfcomp <- left_join(ANCOdf1, ANCOdf2, by = c("Participant.ID", "Allocation"))

# STAI.S

ANCOVA_STAI.S <- aov(STAI.S.Total.Post ~ Allocation + STAI.S.Total.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_STAI.S)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(STAI.S.Total.Pre, type = "mean_sd")

# PANAS.Neg

ANCOVA_PANAS.Neg <- aov(PANAS.negative.Post ~ Allocation + PANAS.negative.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_PANAS.Neg)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(PANAS.negative.Post, type = "mean_sd")

# PANAS.Pos

ANCOVA_PANAS.Pos <- aov(PANAS.positive.Post ~ Allocation + PANAS.positive.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_PANAS.Pos)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(PANAS.positive.Pre, type = "mean_sd")

# VAS.Neg

ANCOVA_VAS.Neg <- aov(VAS.negative.Post ~ Allocation + VAS.negative.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_VAS.Neg)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(VAS.negative.Post, type = "mean_sd")

# VAS.Pos

ANCOVA_VAS.Pos <- aov(VAS.positive.Post ~ Allocation + VAS.positive.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_VAS.Pos)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(VAS.positive.Post, type = "mean_sd")

# DARS

ANCOVA_DARS <- aov(DARS.Total.Post ~ Allocation + DARS.Total.Pre + Error(Participant.ID), data = ANCOdfcomp)

summary(ANCOVA_DARS)

ANCOdfcomp %>%
  group_by(Allocation) %>%
  get_summary_stats(DARS.Total.Post, type = "mean_sd")

### All non-significant
```
```{r pressure, echo=FALSE}
# Further plots for self-report measures

State_Anxiety_plot <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = STAI.S.Total, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("State anxiety score (STAI)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

DARS_plot <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = DARS.Total, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Anhedonia score (DARS)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

PANAS_Neg <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = PANAS.negative, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Negative items (PANAS)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

PANAS_Pos <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = PANAS.positive, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Positive items (PANAS)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

VAS_neg <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = VAS.negative, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Negative items (VAS)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

VAS_pos <- Questionnaires_df_master_post %>% ggplot(aes(x = Allocation, y = VAS.positive, fill = Allocation)) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Positive items (VAS)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15))

CombinedPlots_2 <- plot_grid(DARS_plot, PANAS_Neg, PANAS_Pos, State_Anxiety_plot, VAS_neg, VAS_pos, align = "v", ncol = 3, label_size = 20)
````

```{r pressure, echo=FALSE}
# All items

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Aggregate.Perc.2 ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

##

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Motiv.Perc ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

##

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Mood ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

##

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Execu.Perc ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

# Significant interaction - Post-hoc EMM

SUBCOG_df_master$Time <- as.numeric(SUBCOG_df_master$Time)

SUBCOG_df_master$Time <- as.factor(SUBCOG_df_master$Time)

model_linear <- lmer(SUBCOG.Execu.Perc ~ Allocation + Time + Allocation:Time + (1 | Participant.ID), data = SUBCOG_df_master)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Time)

pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

# No significant difference in pairwise comparisons across individual timepoints.

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

##

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Att.Perc ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

##

Vas_Pos_Model <- with(SUBCOG_df_master, lmer(SUBCOG.Memory.Perc ~ Allocation + Time + Allocation:Time + (1 | Participant.ID),
  control = lmerControl(optimizer = "bobyqa")
))

summary(Vas_Pos_Model, conf.int = TRUE)

confint(Vas_Pos_Model, method = "Wald")

# Supplementary Fig 17

SUBCOG_agg_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Aggregate.Perc.2), SE = std.error(SUBCOG.Aggregate.Perc.2), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Subjective cognition aggregate (%)\n") +
  xlab("\nTime\n") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank()
  )

SUBCOG_motiv_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Motiv.Perc), SE = std.error(SUBCOG.Motiv.Perc), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Motivation subscale (%)\n") +
  xlab("\nTime\n") +
  theme_minimal() +
  ylim(57, 65) +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank(),
  )

SUBCOG_mood_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Mood), SE = std.error(SUBCOG.Mood), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Mood subscale (%)\n") +
  xlab("\nTime\n") +
  ylim(52, 65) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank(),
  )

SUBCOG_exec_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Execu.Perc), SE = std.error(SUBCOG.Execu.Perc), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Executive function subscale (%)\n") +
  xlab("\nTime\n") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank(),
  )

SUBCOG_att_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Att.Perc), SE = std.error(SUBCOG.Att.Perc), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Selective attention subscale (%)\n") +
  xlab("\nTime\n") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank()
  )

SUBCOG_mem_fig <- SUBCOG_df_master %>%
  group_by(Allocation, Time) %>%
  summarize(value = mean(SUBCOG.Memory.Perc), SE = std.error(SUBCOG.Memory.Perc), .groups = "drop") %>%
  ggplot(aes(Time, value, group = Allocation)) +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(x = Time, ymin = value - SE, ymax = value + SE, color = Allocation), width = 0.25) +
  geom_point(aes(color = Allocation, shape = Allocation), size = 2.5, alpha = 0.8) +
  geom_line(aes(color = Allocation, linetype = Allocation), size = 1.2) +
  geom_ribbon(aes(
    ymin = value - SE,
    ymax = value + SE, fill = Allocation
  ), color = NA, alpha = 0.095, show.legend = FALSE) +
  scale_shape_manual(values = c(19, 15)) +
  scale_fill_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 2),
    margin_top = 0.05
  ) +
  labs(title = "") +
  ylab("Memory subscale (%)\n") +
  xlab("\nTime\n") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank()
  )

SuppFig17 <- plot_grid(SUBCOG_motiv_fig, SUBCOG_mood_fig, SUBCOG_exec_fig, SUBCOG_att_fig, SUBCOG_mem_fig, SUBCOG_agg_fig, align = "v", ncol = 3, label_size = 20)
```
