---
title: "Presentation PILT Script"
author: "Michael Colwell"
date: '2024-04-10'
output: html_document
---

##PILT pre-processing script

This is the behavioural processing script for the Probabilistic Instrumental Learning Task (PILT), modified for the PEACE study by Michael Colwell (michael.colwell@psych.ox.ac.uk).

This script for for behavioural data only; for computational modelling analysis, see '/PILT_Reinforcement_Learning_Mod/PILT_comp_analysis.Rmd'.

Before proceeding it is important to make sure all your files are labelled with the participant ID in the following format:

P00X
or 
p0Xx

It is robust to upper-case/lower-case letters, however if there are too many 0s it will fail to load it in.

If you have a follow-up visit, make sure the file name includes 'v2', and this will be sorted considered a follow-up or PRE visit.

##Chunk 0: Set-up chunk

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

##Chunk 1: Loading required R packages

```{r Chunk 1 - Libraries Setup, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggplot2)
library(car)
library(ggbeeswarm)
library(ggrepel)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(sdamr)
library(cowplot)
library(lme4)
library(stringr)
library(ggridges)
library(viridis)
library(stringr)
library(effectsize)
library(lmerTest)
library(ggdist)
library(moments)
```

#Chunk 2: Loading files into memory and creating an aggregate

```{r Chunk 2 - Loading Files, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/PILT_nonmodel")

# Create an empty data frame to store the combined data
combined_df <- data.frame()

# Get a list of all .dat files in the directory
dat_files <- list.files(pattern = "\\.dat$")

# Loop through each .dat file
for (file in dat_files) {
  # Read the file using readLines()
  lines <- readLines(file)

  # Remove the first three lines
  lines <- lines[-(1:3)]

  # Extract the file name
  file_name <- sub("\\.dat$", "", file)

  # Check if the file name contains P001, P002, etc.
  if (grepl("[Pp]\\d{3}", file_name)) {
    # Check if there are lines remaining
    if (length(lines) > 0) {
      # Replace blank spaces with NA in each line
      lines <- lapply(lines, function(line) {
        words <- strsplit(line, "\\s+")[[1]]
        words[words == ""] <- NA
        return(words)
      })

      # Find the maximum number of elements in a line
      max_elements <- max(sapply(lines, length))

      # Create a matrix to store the data
      data_matrix <- matrix(nrow = length(lines), ncol = max_elements)

      # Fill the matrix with the data from the lines
      for (i in seq_along(lines)) {
        row <- lines[[i]]
        data_matrix[i, 1:length(row)] <- row
      }

      # Convert the matrix to a data frame
      df <- as.data.frame(data_matrix, stringsAsFactors = FALSE) # Ensure strings are treated as characters

      # Add a column with the file name to the data frame
      df <- cbind(FileName = file_name, df)

      # Bind the data to the combined data frame
      combined_df <- bind_rows(combined_df, df)
    }
  }
}

# Move first row as column names
colnames(combined_df)[-1] <- combined_df[1, -1]
combined_df <- combined_df[-1, ]

# Move values from "win_out" to "loss_out" based on "trial_type"
combined_df$loss_out[combined_df$trial_type == 2] <- combined_df$win_out[combined_df$trial_type == 2]
combined_df$win_out[combined_df$trial_type == 2] <- NA

## You'll need to change this one manually##
combined_df <- rename(combined_df, file_name = FileName)

# Split 'file_name' column into 'Participant.ID' and 'Visit'
combined_df <- combined_df %>%
  mutate(
    ID <- str_extract(file_name, "(?<=^)[Pp]0*\\d+"),
    PRE.POST = ifelse(str_detect(file_name, "v2"), "POST", "PRE")
  )

# Prune 'Participant.ID' column to first few letters
combined_df$ID <- str_sub(combined_df$ID, 1, 4)

# Convert 'Participant.ID' column to uppercase
combined_df$ID <- toupper(combined_df$ID)

combined_df <- combined_df %>%
  select(ID, PRE.POST, everything())

combined_df_for_money <- combined_df

value_to_remove <- "run_number" # Specify the value to be removed
combined_df <- combined_df[!(combined_df$run_number == value_to_remove), ]

value_to_remove2 <- "Total" # Specify the value to be removed
combined_df <- combined_df[!(combined_df$run_number == value_to_remove2), ]

## Above code is duplicated intentionally.

PILT <- combined_df

## Check all the participant data is there

unique_strings <- unique(combined_df$ID)
summary <- data.frame(String = unique_strings, Count = length(unique_strings))

print(summary)

rm(data_matrix, df, lines, dat_files, file, file_name, i, max_elements, row, combined_df)
```

#Chunk Extra: DF just for amount of money won over participant

```{r Chunk 2 - Loading Files, message=FALSE, warning=FALSE, include=FALSE}
# Money value is on line 185

combined_df_for_money <- subset(combined_df_for_money, run_number == "Total")

combined_df_for_money$MoneyEarned <- as.numeric(combined_df_for_money$outcome_type)

columns_to_keep <- c("ID", "PRE.POST", "MoneyEarned")

Money_Clean <- combined_df_for_money[, columns_to_keep]

Money_Clean$PRE.POST <- recode_factor(Money_Clean$PRE.POST, "PRE" = "Baseline")
Money_Clean$PRE.POST <- recode_factor(Money_Clean$PRE.POST, "POST" = "Post")

Money_Clean_pre <- Money_Clean %>% filter(!str_detect(PRE.POST, "Post"))
Money_Clean_post <- Money_Clean %>% filter(!str_detect(PRE.POST, "Baseline"))
```

#Optional chunk: Overlapping simulated choice probabilities from fitted data.

```{r Chunk 2 - Loading Files, message=FALSE, warning=FALSE, include=FALSE}
# Not required - Synthetic data published in previous study (Colwell et al., 2024)
```

#Chunk 3: Initial pre-processing of data to prepare for analyses

```{r Chunk 3 - Initial Preprocessing, message=FALSE, warning=FALSE, include=FALSE}
PILT <- PILT %>% mutate(Optimal_choice = case_when((loss_out == 1) ~ "0", (loss_out == 0) ~ "1", (win_out == 1) ~ "1", (win_out == 0) ~ "0", TRUE ~ "NA"))

# Participant P012 was excluded for data concern issues (task adherence/familiarity issues) -- however, the results remain significant with their inclusion.

removal_df <- subset(PILT, ID != "P012")
PILT <- droplevels(removal_df)

removal_df <- subset(Money_Clean, ID != "P012")
Money_Clean <- droplevels(removal_df)

PILT2 <- PILT

PILT$Optimal_choice <- as.numeric(PILT$Optimal_choice)

PILT <- PILT %>% transform(RT_hits = ifelse(Optimal_choice == 1, reaction_time, NA))

PILT$reaction_time <- as.numeric(PILT$reaction_time)

# Create a seperate df for the learning curve

PILT2$Optimal_choice <- as.numeric(PILT2$Optimal_choice)

# Remove the first third of trials (period of learning), so you only have 20 trials per condition per run - it doesn't matter if you keep them in or remove 30, it remains significant.

PILT$trial_number <- as.numeric(PILT$trial_number)

PILT <- PILT %>% filter(trial_number > 19)

PILT <- PILT %>% select(-file_name)

###
```

#Chunk 4: Further preprocessing the dataframe 

```{r Chunk 5 - Further preprocessing, message=FALSE, warning=FALSE, include=FALSE}
# create overall summary for statistical analysis
# Create another non-summary to plot the curve (further down)

PILT$loss_out <- as.numeric(PILT$loss_out)
PILT$win_out <- as.numeric(PILT$win_out)
PILT$reaction_time <- as.numeric(PILT$reaction_time)
PILT$RT_hits <- as.numeric(PILT$RT_hits)

# There is only one PILT session in the 'PEACE' study (post-administration), therefore remove the 'PRE' label to avoid confusion.
PILT$PRE.POST <- NA

PILT_Analysis_ReportLME <- PILT %>%
  group_by(ID, PRE.POST, trial_type) %>%
  summarise(Optimal.choice = sum(Optimal_choice, na.rm = TRUE), Response.time = mean(reaction_time, na.rm = TRUE), Optimal.choice.perc = mean(Optimal_choice, na.rm = TRUE) * 100, response.time.corr = mean(RT_hits, na.rm = TRUE))

# Divide optimal choices by the total number of trials across all blocks (i.e., 40 * 3, since the first 20 trials are being excluded.)

setwd("C:/Users/micha/Desktop/PEACE_Data_and_Code/Behavioural_Data/Allocation_and_Demographics")

PILT_Analysis_ReportLME$trial_type <- as.factor(PILT_Analysis_ReportLME$trial_type)

##

PILT_Analysis_ReportLME$trial_type <- recode_factor(PILT_Analysis_ReportLME$trial_type, "2" = "Loss trials")

PILT_Analysis_ReportLME$trial_type <- recode_factor(PILT_Analysis_ReportLME$trial_type, "1" = "Win trials")

Demographics <- read.csv("Allocation_And_Demo.csv")

Demographics$ID <- as.factor(Demographics$Participant.ID)

PILT_Analysis_ReportLME <- merge(PILT_Analysis_ReportLME, Demographics, by = "ID")
Money_LME <- merge(Money_Clean, Demographics, by = "ID")

## Add in winstotal condition (not win or loss condition)

## Creating and tidying curve data (CurveData and CurveData are used for creating the learning curves)

CurveData <- PILT2

CurveData$PRE.POST <- recode_factor(CurveData$PRE.POST, "PRE" = "Baseline")

CurveData$PRE.POST <- recode_factor(CurveData$PRE.POST, "POST" = "Post")

CurveData <- merge(CurveData, Demographics, by = "ID")

# Comment this out when you want to look at data from all timepoints
# CurveData <- CurveData %>% filter(!str_detect(PRE.POST, "Baseline"))

CurveData <- CurveData %>% mutate(loss_out2 = case_when((loss_out == 1) ~ "1", (loss_out == 0) ~ "0", TRUE ~ "NA"))

# CurveData <- CurveData %>% mutate(loss_out2 = case_when((loss_out == 1) ~ "0", (loss_out == 0) ~ "1", TRUE ~ "NA"))

# CurveData <- CurveData %>% mutate(loss_out = case_when((loss_out == 1) ~ "0", (loss_out == 0) ~ "1", TRUE ~ "NA"))


# Change to this to make comparison with synthetic data

CurveData$loss_out2 <- as.numeric(CurveData$loss_out2)
CurveData$loss_out2 <- as.numeric(CurveData$loss_out2)
CurveData$trial_number <- as.numeric(CurveData$trial_number)
CurveData$run_number <- as.numeric(CurveData$run_number)

rm(PILT, PILT2)
```

#Chunk 5 (Optional): Running initial data quality tests

```{r Chunk 4 (Optional) - Initial quality checks, echo=FALSE}
# create overall summary for identifying outliers

# Quality checks

# Function to detect outliers
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 3.0 * IQR(x) | x > quantile(x, 0.75) + 3.0 * IQR(x))
}

# Optimal Choices

Optimal_Choice_Plot <- ggplot(PILT_Analysis_ReportLME, aes(x = as.factor(trial_type), y = Optimal.choice.perc)) +
  geom_boxplot(outlier.shape = NA) + # Hide outlier points in boxplot
  geom_point(data = PILT_Analysis_ReportLME[is_outlier(PILT_Analysis_ReportLME$Optimal.choice.perc), ], aes(color = Participant.ID)) +
  geom_text_repel(data = PILT_Analysis_ReportLME[is_outlier(PILT_Analysis_ReportLME$Optimal.choice.perc), ], aes(label = Participant.ID), color = "black", size = 3) + # Label outliers
  labs(
    title = "",
    y = "\nOptimal Choices (%)\n",
    x = "\nTrial Type\n"
  ) +
  theme_minimal() +
  theme(text = element_text(size = 16))

# Time to choice

Optimal_Choice_Plot <- ggplot(PILT_Analysis_ReportLME, aes(x = as.factor(trial_type), y = Response.time)) +
  geom_boxplot(outlier.shape = NA) + # Hide outlier points in boxplot
  geom_point(data = PILT_Analysis_ReportLME[is_outlier(PILT_Analysis_ReportLME$Response.time), ], aes(color = Participant.ID)) +
  geom_text_repel(data = PILT_Analysis_ReportLME[is_outlier(PILT_Analysis_ReportLME$Response.time), ], aes(label = Participant.ID), color = "black", size = 3) + # Label outliers
  labs(
    title = "",
    y = "\nTime to choice (ms)\n",
    x = "\nTrial Type\n"
  ) +
  theme_minimal() +
  theme(text = element_text(size = 16))
```

#Chunk 6: Further parsing the curvedata

```{r Chunk 6 - Further parsing the curvedata, message=FALSE, warning=FALSE, include=FALSE}
# Initialize count variable
count <- 1

# Initialize previous run number variable
prev_run <- NULL

# Initialize output vector
output <- vector()

# Iterate over each row of the data frame
for (i in 1:nrow(CurveData)) {
  # Check if the 'run_number' has changed from the previous row
  if (!is.null(prev_run) && CurveData$run_number[i] != prev_run) {
    count <- 1
  }

  # Check if the 'trial_type' column contains the specific value (1)
  if (CurveData$trial_type[i] == 1) {
    output <- c(output, count)
    count <- count + 1
  } else {
    output <- c(output, NA)
  }

  # Update previous run number
  prev_run <- CurveData$run_number[i]
}

# Add the output vector as a new column ('win_trial_count') to the data frame
CurveData$win_trial_count <- output

###

# Initialize count variable
count <- 1

# Initialize previous run number variable
prev_run <- NULL

# Initialize output vector
output <- vector()

# Iterate over each row of the data frame
for (i in 1:nrow(CurveData)) {
  # Check if the 'run_number' has changed from the previous row
  if (!is.null(prev_run) && CurveData$run_number[i] != prev_run) {
    count <- 1
  }

  # Check if the 'trial_type' column contains the specific value (1)
  if (CurveData$trial_type[i] == 2) {
    output <- c(output, count)
    count <- count + 1
  } else {
    output <- c(output, NA)
  }

  # Update previous run number
  prev_run <- CurveData$run_number[i]
}

# Add the output vector as a new column ('loss_trial_count') to the data frame
CurveData$loss_trial_count <- output

counts2 <- table(CurveData$loss_trial_count)
counts3 <- table(CurveData$win_trial_count)

print(counts2)
print(counts3)
# Note that there appears to be slightly more win trials overall than loss trials.

rm(PILT, PILT2, count, i, output, prev_run, unique_strings, value_to_remove, value_to_remove2, summary)

## Variable conversion

CurveData$loss_out <- as.numeric(CurveData$loss_out)
CurveData$win_out <- as.numeric(CurveData$win_out)

## Now create reports and merge

WinCurveReport <- CurveData %>%
  group_by(Allocation, win_trial_count, trial_type) %>%
  summarise(Optimal.choice = mean(Optimal_choice, na.rm = TRUE) * 100, SE = sd(Optimal_choice, na.rm = TRUE) / sqrt(n()) * 100)

WinCurveReport_clean <- WinCurveReport[complete.cases(WinCurveReport), ]

names(WinCurveReport_clean)[2] <- "trial_number"

LossCurveReport <- CurveData %>%
  group_by(Allocation, loss_trial_count, trial_type) %>%
  summarise(Optimal.choice = mean(loss_out2, na.rm = TRUE) * 100, SE = sd(Optimal_choice, na.rm = TRUE) / sqrt(n()) * 100)

LossCurveReport_clean <- LossCurveReport[complete.cases(LossCurveReport), ]

names(LossCurveReport_clean)[2] <- "trial_number"

rm(LossCurveReport, WinCurveReport)

CompleteCurve <- bind_rows(WinCurveReport_clean, LossCurveReport_clean)

## Create final df for Learning Curve

CompleteCurve$Grp <- paste(CompleteCurve$Allocation, CompleteCurve$trial_type, sep = "_")

############################################

# Another curve for comparison/split

############################################

## Now create reports and merge

WinCurveReport <- CurveData %>%
  group_by(Allocation, win_trial_count, trial_type) %>%
  summarise(Optimal.choice = mean(Optimal_choice, na.rm = TRUE) * 100, SE = sd(Optimal_choice, na.rm = TRUE) / sqrt(n()) * 100)

WinCurveReport_clean <- WinCurveReport[complete.cases(WinCurveReport), ]

names(WinCurveReport_clean)[2] <- "trial_number"

LossCurveReport <- CurveData %>%
  group_by(Allocation, loss_trial_count, trial_type) %>%
  summarise(Optimal.choice = mean(loss_out2, na.rm = TRUE) * 100, SE = sd(Optimal_choice, na.rm = TRUE) / sqrt(n()) * 100)

LossCurveReport_clean <- LossCurveReport[complete.cases(LossCurveReport), ]

names(LossCurveReport_clean)[2] <- "trial_number"

rm(LossCurveReport, WinCurveReport)

CompleteCurve <- bind_rows(WinCurveReport_clean, LossCurveReport_clean)

## Create final df for Learning Curve

CompleteCurve$Grp <- paste(CompleteCurve$Allocation, CompleteCurve$trial_type, sep = "_")

############################################
```

#Chunk 6.5: Preparing model-fit curve data (probability of choice across each trial)

```{r Chunk 6 - Further parsing the curvedata, message=FALSE, warning=FALSE, include=FALSE}
# Not required - Synthetic data published in previous study (Colwell et al., 2024)
```

#Chunk 7 (Optional): Generation of learning curves with synthetic data; comparison between synthetic and real data

```{r Chunk 6 - Further parsing the curvedata, message=FALSE, warning=FALSE, include=FALSE}
# Not required - Synthetic data published in previous study (Colwell et al., 2024)
```



#Chunk 7.5: Generation of figures for report

```{r Chunk 7 - Generation of figures for report, echo=FALSE}
# Learning curve for publication

# Figure 5B

CurveUnified <- ggplot(CompleteCurve, aes(trial_number, Optimal.choice, group = Grp, colour = Allocation, linetype = Allocation)) +
  geom_segment(aes(x = 10, xend = 30, y = 50, yend = 50), linetype = "dotted", color = "azure3") +
  geom_vline(xintercept = 10, linetype = "dotted", color = "azure3") +
  geom_line() +
  geom_point(aes(shape = Allocation, linetype = NA), size = 2.75, alpha = 0.77) +
  geom_ribbon(aes(
    ymin = Optimal.choice - SE,
    ymax = Optimal.choice + SE, fill = Allocation
  ), color = NA, alpha = 0.11, show.legend = FALSE) +
  theme_minimal() +
  scale_shape_manual(values = c(19, 15)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  ylab("High probability stimulus selected (%)\n") +
  xlab("Trial number\n") +
  annotate("text", x = 15, y = 70, label = "\nWin trials", size = 3.5, color = "#333333") +
  annotate("text", x = 15, y = 16, label = "\nLoss trials", size = 3.5, color = "#333333") +
  theme(text = element_text(size = 12), plot.margin = unit(c(0, 0, 0, 0), "cm"), axis.title = element_text(size = 12), legend.text = element_text(size = 10), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 10.5), legend.position = c(0.875, 0.59), legend.title = element_blank())

# Figure 5D

Boxplot_Optimal <- PILT_Analysis_ReportLME %>% ggplot(aes(x = Allocation, y = Optimal.choice.perc, fill = Allocation)) +
  facet_wrap(~trial_type) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c("***" = 0.001, "**" = 0.01, "*" = 0.05, " " = 0.20, " " = 2),
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Optimal choices (%)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15)) +
  ylim(40, NA)

## Plot for response time across paradigms

# Supplementary Fig. 14A

Boxplot_Optimal <- PILT_Analysis_ReportLME %>% ggplot(aes(x = Allocation, y = Response.time, fill = Allocation)) +
  facet_wrap(~trial_type) +
  stat_slab(
    side = "right", scale = 0.55, show.legend = F,
    position = position_dodge(width = .8), alpha = 0.5,
    aes(fill_ramp = stat(level)), .width = c(.50, .95, 1)
  ) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  geom_signif(
    comparisons = list(c("ACTIVE", "PLACEBO")),
    p.adjust.method = "bonferroni",
    map_signif_level = c(" " = 0.001, " " = 0.01, "*" = 0.05, " " = 0.20, " " = 2), # Removing asterisk to align with EMM
    margin_top = 0.05, textsize = 12
  ) +
  labs(title = " ") +
  ylab("Time to choice (ms)\n") +
  xlab(" ") +
  theme_minimal() +
  theme(
    legend.position = "none", text = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title = element_text(size = 20), axis.text.x = element_text(size = 14), strip.text = element_text(hjust = 0.41, vjust = 1, size = 14.5),
    panel.spacing = unit(-8, "lines")
  ) +
  stat_boxplot(
    geom = "errorbar",
    width = 0.15
  ) +
  geom_point(position = position_jitternudge(
    jitter.width = 0.125, jitter.height = -0.3, nudge.x = -0.265, seed = 123
  ), aes(color = Allocation, shape = Allocation), size = 4.4, stroke = 0.2, alpha = 0.5) +
  scale_shape_manual(values = c(19, 15)) +
  ylim(40, NA)

##
```

#Inferential analyses: ANOVA, emmeans and descriptive stats

```{r Chunk 8 - ANCOVA-type LME inferrential analyses, emmeans and descriptive stats, echo=FALSE}
# Checking distribution

x <- PILT_Analysis_ReportLME$Optimal.choice.perc

# skewness
skew_val <- skewness(x, na.rm = TRUE)

kurt_val <- kurtosis(x, na.rm = TRUE) # excess kurtosis by default

c(skew_val = skew_val, kurt_val = kurt_val)


# Inferential analysis

# Optimal Choice

Accuracy_Model <- aov(Optimal.choice.perc ~ Allocation + trial_type + Allocation:trial_type + Error(Participant.ID), data = PILT_Analysis_ReportLME)

summary(Accuracy_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Optimal.choice.perc ~ Allocation + trial_type + Allocation:trial_type + (1 | Participant.ID), data = PILT_Analysis_ReportLME)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | trial_type)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

PILT_Analysis_ReportLME %>%
  group_by(trial_type, Allocation) %>%
  get_summary_stats(Optimal.choice.perc, type = "mean_sd")

####

# Time to choice

Accuracy_Model <- aov(Response.time ~ Allocation + trial_type + Allocation:trial_type + Error(Participant.ID), data = PILT_Analysis_ReportLME)

summary(Accuracy_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Response.time ~ Allocation + trial_type + Allocation:trial_type + (1 | Participant.ID), data = PILT_Analysis_ReportLME)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~Allocation)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

PILT_Analysis_ReportLME %>%
  group_by(trial_type, Allocation) %>%
  get_summary_stats(Response.time, type = "mean_sd")

########################################################################################################################

# Money analysis

Money_model <- aov(MoneyEarned ~ Allocation, data = Money_LME)

summary(Money_model)

model_linear <- lm(MoneyEarned ~ Allocation, data = Money_LME)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

Money_LME %>%
  group_by(Allocation) %>%
  get_summary_stats(MoneyEarned, type = "mean_sd")

####
```

```
